\documentclass[11pt,letterpaper,sans]{moderncv}

\usepackage{graphicx}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{textcomp}
\usepackage{units}
\usepackage{lineno}
\usepackage{rotating}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{comment}
\usepackage{xcolor}
\usepackage[gen]{eurosym}


\moderncvstyle{banking}                           
\moderncvcolor{blue}    

\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,bindingoffset=0cm]{geometry}
\setlength{\hintscolumnwidth}{3cm}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{lastpage}
\usepackage{mathabx}
\cfoot{{\color{gray} Page \thepage\ of \pageref{LastPage}}}


\def\prd{{Phys. Rev.} D}
\def\PRL{{Phys.Rev.} Lett}
\def\apjl{{Astrophys. J.} Lett}
\def\apj{{Astrophys. J.}}
\def\CQG{{Class. Quantum Grav.}}
\def\aaps{{A\&AS}}
\def\pasj{{PASJ}}
\def\mnras{{MNRAS}} 
\def\aapr{{A\&ARv}}
\def\aap{{A\&A}}
\def\na{{New Astronomy}}
\def\ptp{{Progress of Theoretical Physics}}
\def\apjs{{ApJS}}
\def\araa{{ARA\&A}}
\def\ssr{{Space Sci. Rev.}} 

\newcommand{\cvreference}[9]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
   \ifthenelse{\equal{#6}{}}{}{#6\newline}%
  \ifthenelse{\equal{#7}{}}{}{#7\newline}%
  \ifthenelse{\equal{#8}{}}{}{\emailsymbol~{\footnotesize \texttt{\emaillink[]{#8}}}\newline}
    \ifthenelse{\equal{#9}{}}{}{\phonesymbol~#9}}
 
%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{\huge{Stephen~R.}} % Your first name
\familyname{\huge{Taylor}} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{\huge{Publications}}
\address{Department of Physics \& Astronomy, Vanderbilt University}{6301 Stevenson Center, Nashville, TN 37235, USA}
\phone[mobile]{+1~(626)~689~5832}
\email{stephen.r.taylor@vanderbilt.edu}
\homepage{stevertaylor.github.io}
\social[github]{stevertaylor}
%\social[linkedin][linkedin.com/in/stephen-taylor-a8164787]{stephen-taylor $\;\;\bullet\;\;$ \today}
\social[linkedin][linkedin.com/in/stephen-taylor-a8164787]{stephen-taylor}

\lhead{{\color{gray} \fontsize{10}{22}\mdseries\upshape{Stephen~R.~Taylor}}}
\rhead{{\color{gray} \fontsize{10}{10}\mdseries\upshape{stephen.r.taylor@vanderbilt.edu}}}

%\definecolor{color1}{HTML}{1f77b4}
%\hypersetup{urlcolor=color1,linkcolor=color1}


\begin{document}
\makecvtitle 

\vspace{-2mm}
%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

%\section{Full Publication List} %\vspace{-0.3cm} 

\cvitem{}
{
\begin{tabular}{rcl}
\textbf{Counts}: &\hspace{0.3cm} &{\textbf{52} papers published in major peer-reviewed journals} \\
& &{(out of which \textbf{12} are first-authored papers, and \textbf{4} papers were covered by press releases).}
\end{tabular}
}

$\bullet$ \textbf{Total number of citations:} 3973 (using Google Scholar), \textbf{h-index:} 31, \textbf{i10-index:} 47

$\bullet$ \textbf{Metrics} available at Google Scholar: {\color{color1} \href{http://bit.ly/2hgVCzb}{http://bit.ly/2hgVCzb}}.

$\bullet$ \textbf{Full list of publications} can be found below, and at {\color{color1} \href{http://bit.ly/2fF3yGI}{http://bit.ly/2fF3yGI}}.

\vspace{0.4cm}
%\subsection{Submitted} \vspace{-0.3cm}
%
%\cvitem{}{\small
%\hspace{-2cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%\textbf{1.} & & ``\textit{Mining Gravitational-wave Catalogs To Understand Binary Stellar Evolution: A New Hierarchical Bayesian Framework}'' \\ 
%&&\textit{\textbf{S.~R.~Taylor}} and D.~Gerosa \\
%&& \href{https://arxiv.org/abs/1806.08365}{{\color{color1} Submitted to Phys.~Rev.~D, arXiv:1806.08365 (2018)}}  
%\end{longtable}
%}

%\vspace{-0.6cm}

Articles with significant student leadership (at time of publication) have student names \underline{underlined}.

\subsection{Submitted} \vspace{-0.3cm}
\cvitem{}{\small
\hspace{-2cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
\textbf{4.} & & ``\textit{Discriminating between different scenarios for the formation and evolution of massive black holes with LISA}'' \\ 
&&\underline{A.~Toubiana}, \underline{K.~W.~K.~Wong}, S.~Babak, E.~Barausse, E.~Berti, J.~R.~Gair, S.~Marsat, \textit{\textbf{S.~R.~Taylor}} \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2021arXiv210613819T/arxiv:2106.13819}{{\color{color1} arXiv:2106.13819}}  \vspace{0.09cm}\\
\textbf{3.} & & ``\textit{Searching For Gravitational Waves From Cosmological Phase Transitions With The NANOGrav 12.5-year dataset}'' \\ 
&&Z.~Arzoumanian, P.~T.~Baker, H.~Blumer [and 62 others, including \textit{\textbf{S.~R.~Taylor}} in core analysis team] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2021arXiv210413930A/arxiv:2104.13930}{{\color{color1} arXiv:2104.13930}}  \vspace{0.09cm}\\
&& \textcolor{red}{$\bullet$} $13$ citations. \vspace{0.09cm}\\
\textbf{2.} & & ``\textit{Bayesian Forecasts for Dark Matter Substructure Searches with Mock Pulsar Timing Data}'' \\ 
&&\underline{V.~S.~H.~Lee}, \textit{\textbf{S.~R.~Taylor}}, T.~Trickle, K.~M.~Zurek\\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2021arXiv210405717L/arxiv:2104.05717}{{\color{color1} arXiv:2104.05717}}  \vspace{0.09cm}\\
&& \textcolor{red}{$\bullet$} $4$ citations. \vspace{0.09cm}\\
\textbf{1.} & & ``\textit{Mapping the Gravitational-wave Sky with LISA: A Bayesian Spherical Harmonic Approach}'' \\ 
&&\underline{S.~Banagiri}, \underline{A.~Criswell}, \underline{T.~Kuan}, V.~Mandic, J.~D.~Romano, \textit{\textbf{S.~R.~Taylor}}\\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2021arXiv210300826B/arxiv:2103.00826}{{\color{color1} arXiv:2103.00826}}  \vspace{0.09cm}\\
\end{longtable}
}

\subsection{Publications in major peer-reviewed journals} \vspace{-0.3cm}

\cvitem{}{\small
\hspace{-2cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
\textbf{52.} & & ``\textit{The NANOGrav 11 yr Data Set: Limits on Supermassive Black Hole Binaries in Galaxies within 500 Mpc}'' \\ 
&&Z.~Arzoumanian, P.~T.~Baker, A.~Brazier [and 53 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2021ApJ...914..121A/doi:10.3847/1538-4357/abfcd3}{{\color{color1} The Astrophysical Journal, \textbf{914}, 2 (2021)}}  \vspace{0.09cm}\\
&& \textcolor{red}{$\bullet$} $6$ citations. \vspace{0.09cm}\\
\textbf{51.} & & ``\textit{Astrophysics Milestones for Pulsar Timing Array Gravitational-wave Detection}'' \\ 
&&N.~Pol, \textit{\textbf{S.~R.~Taylor}}, L.~Z.~Kelley, [and 49 others] \\
&& \href{}{{\color{color1} The Astrophysical Journal Letters, \textbf{911}, 2 (2021)}} \\
&& \textcolor{red}{$\bullet$} $18$ citations. \vspace{0.09cm}\\
\textbf{50.} & & ``\textit{The NANOGrav 12.5-year Data Set: Wideband Timing of 47 Millisecond Pulsars}'' \\ 
&&Md~F.~Alam, Z.~Arzoumanian, P.~T.~Baker, [and 67 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2021ApJS..252....5A/doi:10.3847/1538-4365/abc6a1}{{\color{color1} The Astrophysical Journal Supplement Series, \textbf{252}, 1 (2021)}} \\
&& \textcolor{red}{$\bullet$} $34$ citations. \vspace{0.09cm}\\
\textbf{49.} & & ``\textit{The NANOGrav 12.5-year Data Set: Observations and Narrowband Timing of 47 Millisecond Pulsars}'' \\ 
&&Md~F.~Alam, Z.~Arzoumanian, P.~T.~Baker, [and 67 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2021ApJS..252....4A/doi:10.3847/1538-4365/abc6a0}{{\color{color1} The Astrophysical Journal Supplement Series, \textbf{252}, 1 (2021)}} \\
&& \textcolor{red}{$\bullet$} $30$ citations. \vspace{0.09cm}\\
\textbf{48.} & & ``\textit{The NANOGrav 12.5-year Data Set: Search For An Isotropic Stochastic Gravitational-Wave Background}'' \\ 
&&Z.~Arzoumanian, P.~T.~Baker, H.~Blumer, [and 58 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020ApJ...905L..34A/doi:10.3847/2041-8213/abd401}{{\color{color1} The Astrophysical Journal Letters, \textbf{905}, 2 (2020)}} \vspace{0.09cm}\\
&& \textcolor{red}{$\bullet$} $216$ citations. \vspace{0.09cm}\\
\textbf{47.} & & ``\textit{From Bright Binaries To Bumpy Backgrounds: Mapping Realistic Gravitational Wave Skies With Pulsar-Timing Arrays}'' \\ 
&&\textit{\textbf{S.~R.~Taylor}}, R.~van~Haasteren, A.~Sesana \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020PhRvD.102h4039T/doi:10.1103/PhysRevD.102.084039}{{\color{color1} Physical Review D, \textbf{102}, 8 (2020)}} \vspace{0.09cm} \\
&& \textcolor{red}{$\bullet$} $12$ citations. \vspace{0.09cm}\\
\textbf{46.} & & ``\textit{Pulsar Timing Array Constraints on the Merger Timescale of Subparsec Supermassive Black Hole Binary Candidates}'' \\ 
&&\underline{K.~Nguyen}, T.~Bogdanovic, J.~C.~Runnoe, \textit{\textbf{S.~R.~Taylor}}, A.~Sesana, M.~Eracleous, S.~Sigurdsson \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020ApJ...900L..42N/doi:10.3847/2041-8213/abb2ab}{{\color{color1} The Astrophysical Journal Letters, \textbf{900}, 2 (2020)}} \vspace{0.09cm} \\
&& \textcolor{red}{$\bullet$} $4$ citations. \vspace{0.09cm}\\
\textbf{45.} & & ``\textit{Multi-Messenger Gravitational Wave Searches with Pulsar Timing Arrays: Application to 3C66B Using the NANOGrav 11-year Data Set}'' \\ 
&&Z.~Arzoumanian, P.~T.~Baker, A.~Brazier, [and 52 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020ApJ...900..102A/doi:10.3847/1538-4357/ababa1}{{\color{color1} The Astrophysical Journal, \textbf{900}, 2 (2020)}} \\
&& \textcolor{red}{$\bullet$} $12$ citation. \vspace{0.09cm}\\
%\textbf{48.} & & ``\textit{From Bright Binaries To Bumpy Backgrounds: Mapping Realistic Gravitational Wave Skies With Pulsar-Timing Arrays}'' \\ 
%&&\textit{\textbf{S.~R.~Taylor}}, R.~van~Haasteren, A.~Sesana \\
%&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020arXiv200604810T/EPRINT_HTML}{{\color{color1} arXiv:2006.04810}} \vspace{0.09cm} \\
%\textbf{47.} & & ``\textit{Multi-Messenger Gravitational Wave Searches with Pulsar Timing Arrays: Application to 3C66B Using the NANOGrav 11-year Data Set}'' \\ 
%&&Z.~Arzoumanian, P.~T.~Baker, A.~Brazier, [and 52 others, including \textit{\textbf{S.~R.~Taylor}}] \\
%&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020arXiv200507123A/EPRINT_HTML}{{\color{color1} arXiv:2005.07123}} \\
%&& \textcolor{red}{$\bullet$} $1$ citations. \vspace{0.09cm}\\
%\textbf{46.} & & ``\textit{The NANOGrav 12.5-year Data Set: Wideband Timing of 47 Millisecond Pulsars}'' \\ 
%&&Md~F.~Alam, Z.~Arzoumanian, P.~T.~Baker, [and 67 others, including \textit{\textbf{S.~R.~Taylor}}] \\
%&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020arXiv200506495A/EPRINT_HTML}{{\color{color1} arXiv:2005.06495}} \\
%&& \textcolor{red}{$\bullet$} $4$ citations. \vspace{0.09cm}\\
%\textbf{45.} & & ``\textit{The NANOGrav 12.5-year Data Set: Observations and Narrowband Timing of 47 Millisecond Pulsars}'' \\ 
%&&Md~F.~Alam, Z.~Arzoumanian, P.~T.~Baker, [and 67 others, including \textit{\textbf{S.~R.~Taylor}}] \\
%&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020arXiv200506490A/EPRINT_HTML}{{\color{color1} arXiv:2005.06490}} \\
%&& \textcolor{red}{$\bullet$} $3$ citations. \vspace{0.09cm}\\
\textbf{44.} & & ``\textit{Modeling the Uncertainties of Solar System Ephemerides for Robust Gravitational-wave Searches with Pulsar-timing Arrays}'' \\ 
&&M.~Vallisneri, \textit{\textbf{S.~R.~Taylor}}, J.~Simon, [and 61 others] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020ApJ...893..112V/PUB_HTML}{{\color{color1} The Astrophysical Journal, \textbf{893}, 2 (2020)}} \\
&& \textcolor{red}{$\bullet$} $14$ citations. \vspace{0.09cm}\\
\textbf{43.} & & ``\textit{Pulsar timing array signals induced by black hole binaries in relativistic eccentric orbits}'' \\ 
&&A.~Susobhanan, A.~Gopakumar, G.~Hobbs, \textit{\textbf{S.~R.~Taylor}}\\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020PhRvD.101d3022S/PUB_HTML}{{\color{color1} Physical Review D, \textbf{101}, 4 (2020)}} \\
&& \textcolor{red}{$\bullet$} $3$ citations. \vspace{0.09cm}\\
\textbf{42.} & & ``\textit{A pulsar-based time-scale from the International Pulsar Timing Array}'' \\ 
&&G.~Hobbs, L.~Guo, R.~N.~Caballero, [and 56 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020MNRAS.491.5951H/PUB_HTML}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{491}, 4 (2020)}} \\
&& \textcolor{red}{$\bullet$} $17$ citations. \vspace{0.09cm}\\
\textbf{41.} & & ``\textit{The NANOGrav 11 yr Data Set: Evolution of Gravitational-wave Background Statistics}'' \\ 
&&J.~S.~Hazboun, J.~Simon, \textit{\textbf{S.~R.~Taylor}}, [and 60 others] \\
&& \href{https://ui.adsabs.harvard.edu/link_gateway/2020ApJ...890..108H/PUB_HTML}{{\color{color1} The Astrophysical Journal, \textbf{890}, 2 (2020)}} \\
&& \textcolor{red}{$\bullet$} $12$ citations. \vspace{0.09cm}\\
\textbf{40.} & & ``\textit{The NANOGrav 11 yr Data Set: Limits on Gravitational Wave Memory}'' \\ 
&&K.~Aggarwal, Z.~Arzoumanian, P.~T.~Baker, [and 58 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://iopscience.iop.org/article/10.3847/1538-4357/ab6083}{{\color{color1} The Astrophysical Journal, \textbf{889}, 1 (2020)}} \\
&& \textcolor{red}{$\bullet$} $23$ citations. \vspace{0.09cm}\\
\textbf{39.} & & ``\textit{The International Pulsar Timing Array: second data release}'' \\ 
&&B.~B.~Perera, M.~E.~DeCesar, P.~B.~Demorest, [and 72 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://academic.oup.com/mnras/article-abstract/490/4/4666/5586597?redirectedFrom=fulltext}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{490}, 4 (2019)}} \\
&& \textcolor{red}{$\bullet$} $98$ citations. \vspace{0.09cm}\\
\textbf{38.} & & ``\textit{Bayesian cross validation for gravitational-wave searches in pulsar-timing array data}'' \\ 
&&\underline{H.~Wang}, \textit{\textbf{S.~R.~Taylor}}, M.~Vallisneri \\
&& \href{https://academic.oup.com/mnras/article/487/3/3644/5511287}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{487}, 3 (2019)}} \\
&& \textcolor{red}{$\bullet$} $2$ citations. \vspace{0.09cm}\\
\textbf{37.} & & ``\textit{The NANOGrav 11-Year Data Set: Limits on Gravitational Waves from Individual Supermassive Black Hole Binaries}'' \\ 
&&K.~Aggarwal, Z.~Arzoumanian, P.~T.~Baker, [and 60 others, including \textit{\textbf{S.~R.~Taylor}}] \\
&& \href{https://iopscience.iop.org/article/10.3847/1538-4357/ab2236}{{\color{color1} The Astrophysical Journal, \textbf{880}, 1 (2019)}} \\
&& \textcolor{red}{$\bullet$} $71$ citations. \vspace{0.09cm}\\
\textbf{36.} & & ``\textit{Constraining alternative polarization states of gravitational waves from individual black hole binaries using pulsar timing arrays}'' \\ 
&&\underline{L.~O'Beirne}, N.~J.Cornish, S.~J.~Vigeland, \textit{\textbf{S.~R.~Taylor}} \\
&& \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.99.124039}{{\color{color1} Physical Review D, \textbf{99}, 124039 (2019)}} \\
&& \textcolor{red}{$\bullet$} $7$ citations. \vspace{0.09cm}\\
\textbf{35.} & & ``\textit{Catching Gravitational Waves With A Galaxy-sized Net Of Pulsars}'' \\ 
&&\textit{\textbf{S.~R.~Taylor}}\\
&& \href{https://kids.frontiersin.org/article/10.3389/frym.2019.00080}{{\color{color1} Frontiers For Young Minds, \textbf{7}:80 (2019)}} \\
&& \textcolor{red}{$\bullet$} $1$ citation. Pedagogical article aimed at K-12 audience. \vspace{0.09cm}\\
\textbf{34.} & & ``\textit{The Astrophysics Of Nanohertz Gravitational Waves}'' \\ 
&&S.~Burke-Spolaor, \textit{\textbf{S.~R.~Taylor}}, [and 13 others] \\
&& \href{https://arxiv.org/abs/1811.08826}{{\color{color1} The Astronomy and Astrophysics Review (A\&ARv), \textbf{27}, 1 (2019)}} \\
&& \textcolor{red}{$\bullet$} $81$ citations. Comprehensive field review. \vspace{0.09cm}\\
\textbf{33.} & & ``\textit{Mining Gravitational-wave Catalogs To Understand Binary Stellar Evolution: A New Hierarchical Bayesian Framework}'' \\ 
&&\textit{\textbf{S.~R.~Taylor}} and D.~Gerosa \\
&& \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.98.083017}{{\color{color1} Physical Review D, \textbf{98}, 083017 (2018)}} \\
&& \textcolor{red}{$\bullet$} $43$ citations. Featured in PRD's Kaleidoscope review of October 2018. \vspace{0.09cm}\\
\textbf{32.} & & ``\textit{Studying the solar system with the International Pulsar Timing Array}'' \\ 
&&R.~N.~Caballero, Y.~J.~Guo, K.~J.~Lee, [and 77 others, including  \textit{\textbf{S.~R.~Taylor}}]\\
&& \href{https://academic.oup.com/mnras/article-abstract/481/4/5501/5113478?redirectedFrom=fulltext}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{481}, 4 (2018)}}  \\
&& \textcolor{red}{$\bullet$} $15$ citations. \vspace{0.09cm}\\
\textbf{31.} & & ``\textit{The noise-marginalized optimal statistic: A robust hybrid frequentist-Bayesian statistic for the stochastic gravitational-wave background in pulsar timing arrays}'' \\ 
&&S.~J.~Vigeland, \underline{K.~P.~Islo}, \textit{\textbf{S.~R.~Taylor}}, J.~A.~Ellis \\
&& \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.98.044003}{{\color{color1} Physical Review D, \textbf{98}, 044003 (2018)}}  \\
&& \textcolor{red}{$\bullet$} $7$ citations. \vspace{0.09cm}\\
\textbf{30.} & & ``\textit{Improving timing sensitivity in the microhertz frequency regime: limits from PSR J1713+0747 on gravitational waves produced by super-massive black-hole binaries}'' \\ 
&&B.~B.~P.~Perera, B.~W.~Stappers, S.~Babak, [and 25 others. including \textit{\textbf{S.~R.~Taylor}}]\\
&& \href{https://academic.oup.com/mnras/article-abstract/478/1/218/4990951?redirectedFrom=fulltext}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{478}, 1 (2018)}}  \\
&& \textcolor{red}{$\bullet$} $8$ citations. \vspace{0.09cm}\\
\textbf{29.} & & ``\textit{The NANOGrav 11-year Data Set: Pulsar-timing Constraints On The Stochastic Gravitational-wave Background}'' \\ 
&&Z.~Arzoumanian, P.~T.~Baker, A.~Brazier, [and 57 others. \textbf{Corresponding author:} \textit{\textbf{S.~R.~Taylor}}]\\
&& \href{http://iopscience.iop.org/article/10.3847/1538-4357/aabd3b/meta}{{\color{color1} The Astrophysical Journal, \textbf{859}, 1 (2018)}}  \\
&& \textcolor{red}{$\bullet$} $246$ citations. \vspace{0.09cm}\\
\textbf{28.} & & ``\textit{The NANOGrav 11-year Data Set: High-precision timing of 45 Millisecond Pulsars}'' \\ 
&&Z.~Arzoumanian, A.~Brazier, S.~Burke-Spolaor, [and 53 others, including \textit{\textbf{S.~R.~Taylor}}]\\
&& \href{http://iopscience.iop.org/article/10.3847/1538-4365/aab5b0/meta}{{\color{color1} The Astrophysical Journal Supplement Series, \textbf{235}, 2 (2018)}}  \\
&& \textcolor{red}{$\bullet$} $281$ citations. \vspace{0.09cm}\\
\textbf{27.} & & ``\textit{Constraining alternative theories of gravity using pulsar timing arrays}'' \\ 
&&N.~J.~Cornish, \underline{L.~O'Beirne}, \textit{\textbf{S.~R.~Taylor}}, N.~Yunes\\
&& \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.120.181101}{{\color{color1} Physical Review Letters, \textbf{120}, 181101 (2018)}}  \\
&& \textcolor{red}{$\bullet$} $20$ citations. \vspace{0.09cm}\\
\textbf{26.} & & ``\textit{Single Sources in the Low-Frequency Gravitational Wave Sky: properties and time to detection by pulsar timing arrays}'' \\ 
&&\underline{L.~Z.~Kelley}, L.~Blecha, L.~Hernquist, A.~Sesana, \textit{\textbf{S.~R.~Taylor}} \\
&& \href{https://academic.oup.com/mnras/article-abstract/477/1/964/4937809?redirectedFrom=fulltext}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{477}, 1 (2018)}}  \\
&& \textcolor{red}{$\bullet$} $36$ citations. \vspace{0.09cm}\\
\textbf{25.} & & ``\textit{The Local Nanohertz Gravitational-Wave Landscape From Supermassive Black Hole Binaries}'' \\ 
&&C.~Mingarelli, J.~Lazio, A.~Sesana, J.~E.~Greene, J.~A.~Ellis, C.~P.~Ma, S.~Croft, S.~Burke-Spolaor, \textit{\textbf{S.~R.~Taylor}} \\
&& \href{https://www.nature.com/articles/s41550-017-0299-6}{{\color{color1} Nature Astronomy, \textbf{Vol.~1}, p.~886-892 (2017)}} \\
&& \textcolor{red}{$\bullet$} $69$ citations. Press release. \vspace{0.09cm}\\
\textbf{24.} & & ``\textit{The gravitational wave background from massive black hole binaries in Illustris: spectral features and time to detection with pulsar timing arrays}'' \\ 
&& \underline{L.~Z.~Kelley}, L.~Blecha, L.~Hernquist, A.~Sesana, \textit{\textbf{S.~R.~Taylor}} \\ 
&& \href{https://academic.oup.com/mnras/article/471/4/4508/3899130/The-gravitational-wave-background-from-massive}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{471}, 4 (2017)}} \\
&& \textcolor{red}{$\bullet$} $62$ citations. \vspace{0.09cm}\\
\textbf{23.} & & ``\textit{Constraints on the dynamical environments of supermassive black-hole binaries using pulsar-timing arrays}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, \underline{J.~Simon}, L.~Sampson. \\
&& \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.118.181102}{{\color{color1} Physical Review Letters, \textbf{118}, 181102 (2017)}} \\
&& \textcolor{red}{$\bullet$} $29$ citations. \vspace{0.09cm}\\
\textbf{22.} & & ``\textit{All correlations must die: assessing the significance of a stochastic gravitational-wave background in pulsar timing arrays}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}},  L.~Lentati, S.~Babak, S, P.~Brem, J.~.R.~Gair, A.~Sesana, A.~Vecchio \\ 
&&  \href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.95.042002}{{\color{color1} Physical Review D, \textbf{95}, 042002 (2017)}} \\
&& \textcolor{red}{$\bullet$} $25$ citations. \vspace{0.09cm}\\
\textbf{21.} & & ``\textit{High-precision timing of 42 millisecond pulsars with the European Pulsar Timing Array}'' \\ 
&& G.~Desvignes, R.~N.~Caballero, L.~Lentati, [and 40 others, including \textit{\textbf{S.~R.~Taylor}}] \\ 
&&  \href{http://mnras.oxfordjournals.org/content/458/3/3341}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{458}, 3 (2016)}} \\
&& \textcolor{red}{$\bullet$} $179$ citations. \vspace{0.09cm}\\
\textbf{20.} & & ``\textit{From spin noise to systematics: stochastic processes in the first International Pulsar Timing Array data release}'' \\ 
&& L.~Lentati, R.~M.~Shannon, W.~A.~Coles, [and 80 others, including \textit{\textbf{S.~R.~Taylor}}] \\ 
&&  \href{http://mnras.oxfordjournals.org/content/458/2/2161}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{458}, 2 (2016)}} \\
&& \textcolor{red}{$\bullet$} $58$ citations. \vspace{0.09cm}\\
\textbf{19.} & & ``\textit{The International Pulsar Timing Array: first data release}'' \\ 
&& J.~P.~W.~Verbiest, L.~Lentati, G.~Hobbs, [and 89 others, including \textit{\textbf{S.~R.~Taylor}}] \\ 
&&  \href{http://mnras.oxfordjournals.org/content/458/2/1267}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{458}, 2 (2016)}} \\
&& \textcolor{red}{$\bullet$} $238$ citations. \vspace{0.09cm}\\
\textbf{18.} & & ``\textit{The NANOGrav nine-year data set: limits on the isotropic stochastic gravitational wave background}'' \\ 
&& Z.~Arzoumanian, A.~Brazier, S.~Burke-Spolaor, [and 48 others, including \textit{\textbf{S.~R.~Taylor}}] \\ 
&&  \href{http://iopscience.iop.org/article/10.3847/0004-637X/821/1/13/meta}{{\color{color1} The Astrophysical Journal, \textbf{821}, 1 (2016)}} \\
&& \textcolor{red}{$\bullet$} $210$ citations. Press release. \vspace{0.09cm}\\
\textbf{17.} & & ``\textit{The noise properties of 42 millisecond pulsars from the European Pulsar Timing Array and their impact on gravitational-wave searches}'' \\ 
&& R.~N.~Caballero, K.~J.~Lee, L.~Lentati, [and 36 others, including \textit{\textbf{S.~R.~Taylor}}] \\ 
&&  \href{http://mnras.oxfordjournals.org/content/457/4/4421}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{457}, 4 (2016)}} \\
&& \textcolor{red}{$\bullet$} $37$ citations. \vspace{0.09cm}\\
\textbf{16.} & & ``\textit{Are we there yet? Time to detection of nanohertz gravitational waves based on pulsar-timing array limits}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, M.~Vallisneri, J.~A.~Ellis, C.~M.~F.~Mingarelli, T.~J.~W.~Lazio, and R.~van Haasteren \\ 
&&  \href{http://iopscience.iop.org/article/10.3847/2041-8205/819/1/L6/meta}{{\color{color1} The Astrophysical Journal Letters, \textbf{819}, 1 (2016)}} \\
&& \textcolor{red}{$\bullet$} $77$ citations. Press release, and cited in popular-science book. \vspace{0.09cm}\\
\textbf{15.} & & ``\textit{Detecting eccentric supermassive black hole binaries with pulsar timing arrays: resolvable source strategies}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, E.~A.~Huerta, J.~R.~Gair, and S.~T.~McWilliams \\ 
&& \href{http://iopscience.iop.org/article/10.3847/0004-637X/817/1/70/meta}{{\color{color1} The Astrophysical Journal, \textbf{817}, 1 (2016)}} \\
&& \textcolor{red}{$\bullet$} $22$ citations. \vspace{0.09cm}\\
\textbf{14.} & & ``\textit{European Pulsar Timing Array limits on continuous gravitational waves from individual supermassive black hole binaries}'' \\ 
&& S.~Babak, A.~Petiteau, A.~Sesana, P.~Brem, P.~A.~Rosado, \textit{\textbf{S.~R.~Taylor}}, [and 30 others] \\ 
&& \href{http://mnras.oxfordjournals.org/content/455/2/1665}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{455}, 2 (2016)}} \\
&& \textcolor{red}{$\bullet$} $120$ citations. \vspace{0.09cm}\\
\textbf{13.} & & ``\textit{Mapping gravitational-wave backgrounds of arbitrary polarisation using pulsar timing arrays}'' \\ 
&& J.~R.~Gair, J.~D.~Romano, and \textit{\textbf{S.~R.~Taylor}} \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.92.102003}{{\color{color1} Physical Review D, \textbf{92}, 102003 (2015)}} \\
&& \textcolor{red}{$\bullet$} $25$ citations. \vspace{0.09cm}\\
\textbf{12.} & & ``\textit{European Pulsar Timing Array limits on an isotropic stochastic gravitational-wave background}'' \\ 
&& L.~Lentati, \textit{\textbf{S.~R.~Taylor}}, C.~M.~F.~Mingarelli, [and 33 others] \\ 
&& \href{http://mnras.oxfordjournals.org/content/453/3/2576}{{\color{color1} Monthly Notices of the Royal Astronomical Society, \textbf{453}, 3 (2015)}} \\
&& \textcolor{red}{$\bullet$} $304$ citations. \vspace{0.09cm}\\
\textbf{11.} & & ``\textit{Detection of eccentric supermassive black hole binaries with pulsar timing arrays: signal-to-noise ratio calculations}'' \\ && E.~A.~Huerta, S.~T.~McWilliams, J.~R.~Gair, and \textit{\textbf{S.~R.~Taylor}} \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.92.063010}{{\color{color1} Physical Review D, \textbf{92}, 063010 (2015)}} \\
&& \textcolor{red}{$\bullet$} $37$ citations. \vspace{0.09cm}\\
\textbf{10.} & & ``\textit{Phase-coherent mapping of gravitational-wave backgrounds using ground-based laser interferometers}'' \\ 
&& J.~D.~Romano, \textit{\textbf{S.~R.~Taylor}}, N.~J.~Cornish, J.~Gair, C.~M.~F.~Mingarelli, and R.~van Haasteren \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.92.042003}{{\color{color1} Physical Review D, \textbf{92}, 042003 (2015)}} \\
&& \textcolor{red}{$\bullet$} $18$ citations. \vspace{0.09cm}\\
\textbf{9.} & & ``\textit{Limits on anisotropy in the nanohertz stochastic gravitational wave background}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, C.~M.~F.~Mingarelli, J.~R.~Gair, [and 32 others] \\ 
&& \href{http://journals.aps.org/prl/abstract/10.1103/PhysRevLett.115.041101}{{\color{color1} Physical Review Letters, \textbf{115}, 041101 (2015)}} \\
&& \textcolor{red}{$\bullet$} $45$ citations. \vspace{0.09cm}\\
\textbf{8.} & & ``\textit{Estimating the sensitivity of pulsar timing arrays}'' \\ 
&& \underline{C.~J.~Moore}, \textit{\textbf{S.~R.~Taylor}}, and J.~R.~Gair \\ 
&& \href{http://iopscience.iop.org/article/10.1088/0264-9381/32/5/055004/meta}{{\color{color1} Classical and Quantum Gravity, \textbf{32}, 5 (2015)}} \\
&& \textcolor{red}{$\bullet$} $37$ citations. \vspace{0.09cm}\\
\textbf{7.} & & ``\textit{Accelerated Bayesian model-selection and parameter-estimation in continuous gravitational-wave searches with pulsar-timing arrays}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, J.~A.~Ellis, and J.~R.~Gair \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.90.104028}{{\color{color1} Physical Review D, \textbf{90}, 104028 (2014)}} \\
&& \textcolor{red}{$\bullet$} $27$ citations. \vspace{0.09cm}\\
\textbf{6.} & & ``\textit{Mapping gravitational-wave backgrounds using methods from CMB analysis: Application to pulsar timing arrays}'' \\ 
&& J.~R.~Gair, J.~D.~Romano, \textit{\textbf{S.~R.~Taylor}}, and C.~M.~F.~Mingarelli \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.90.082001}{{\color{color1} Physical Review D, \textbf{90}, 082001 (2014)}} \\
&& \textcolor{red}{$\bullet$} $56$ citations. PRD Editors' Suggestion.\vspace{0.09cm}\\
\textbf{5.} & & ``\textit{Searching for anisotropic gravitational-wave backgrounds using pulsar timing arrays}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}} and J.~R.~Gair \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.88.084001}{{\color{color1} Physical Review D, \textbf{88}, 084001 (2013)}} \\
&& \textcolor{red}{$\bullet$} $55$ citations. \vspace{0.09cm}\\
\textbf{4.} & & ``\textit{Hyper-efficient model-independent Bayesian method for the analysis of pulsar timing data}'' \\ 
&& L.~Lentati, P.~Alexander, M.~P.~Hobson, \textit{\textbf{S.~R.~Taylor}}, J.~Gair, S.~T.~Balan, and R.~van Haasteren \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.87.104021}{{\color{color1} Physical Review D, \textbf{87}, 104021 (2013)}} \\
&& \textcolor{red}{$\bullet$} $61$ citations. \vspace{0.09cm}\\
\textbf{3.} & & ``\textit{Weighing the evidence for a gravitational-wave background in the first International Pulsar Timing Array data challenge}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, J.~R.~Gair, and L.~Lentati \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.87.044035}{{\color{color1} Physical Review D, \textbf{87}, 044035 (2013)}} \\
&& \textcolor{red}{$\bullet$} $14$ citations. \vspace{0.09cm}\\
\textbf{2.} & & ``\textit{Cosmology with the lights off: standard sirens in the Einstein Telescope era}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}} and J.~R.~Gair \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.86.023502}{{\color{color1} Physical Review D, \textbf{86}, 023502 (2012)}} \\
&& \textcolor{red}{$\bullet$} $102$ citations. \vspace{0.09cm}\\
\textbf{1.} & & ``\textit{Cosmology using advanced gravitational-wave detectors alone}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, J.~R.~Gair, and I.~Mandel \\ 
&& \href{http://journals.aps.org/prd/abstract/10.1103/PhysRevD.85.023535}{{\color{color1} Physical Review D, \textbf{85}, 023535 (2012)}} \\
&& \textcolor{red}{$\bullet$} $96$ citations. \vspace{0.09cm}\\
\end{longtable}
}

\subsection{Books, book chapters, conference proceedings, white papers, and online articles} \vspace{-0.4cm}

\cvitem{}{\small
\hspace{-2cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
\textbf{11.} & & ``\textit{The Nanohertz Gravitational Wave Astronomer}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}\\ 
&& {\color{color1} \href{https://ui.adsabs.harvard.edu/link_gateway/2021arXiv210513270T/arxiv:2105.13270}{Technical book to be published by Taylor \& Francis, arXiv:2105.13270}} \vspace{0.09cm}\\
\textbf{10.} & & ``\textit{Inferring the properties of a population of compact binaries in presence of selection effects}'' \\ 
&& S.~Vitale, D.~Gerosa, W.~M.~Farr, \textit{\textbf{S.~R.~Taylor}}\\ 
&& {\color{color1} \href{https://ui.adsabs.harvard.edu/link_gateway/2020arXiv200705579V/arxiv:2007.05579}{Chapter of ``Handbook of Gravitational Wave Astronomy'' [Eds. C.~Bambi, S.~Katsanevas, K.~Kokkotas; Springer Singapore, (2021)], arXiv:2007.05579}} \vspace{0.09cm}\\
\textbf{9.} & & ``\textit{Fundamental Physics with Pulsar Timing Arrays}'' \\ 
&& X.~Siemens, J.~Hazboun, P.~T.~Baker, S.~Burke-Spolaor, T.~Dolch, E.~Howard, D.~R.~Madison, C.~Mingarelli, J.~Simon, T.~Smith, \textit{\textbf{S.~R.~Taylor}}; for the NANOGrav Collaboration\\ 
&& {\color{color1} \href{https://www.snowmass21.org/docs/files/summaries/CF/SNOWMASS21-CF7_CF2_Xavier_Siemens-149.pdf}{Submitted to the Particle Physics Community Planning Exercise (a.k.a ``SnowMass'') 2021 LOI call}} \vspace{0.09cm}\\
\textbf{8.} & & ``\textit{NANOGrav Education and Outreach: Growing a Diverse and Inclusive Collaboration for Low-Frequency Gravitational Wave Astronomy}'' \\ 
&& The NANOGrav Collaboration; P.~T.~Baker, H.~Blumer, A.~Brazier, S.~Chatterjee, B.~Christy, F.~Crawford, M.~E.~DeCesar, T.~Dolch, N.~E.~Garver-Daniels, J.~S.~Hazboun, K.~Holley-Bockelmann, D.~L.~Kaplan, J.~S.~Key, T.~C.~Klein, M.~T.~Lam, N.~Lewandowska, D.~R.~Lorimer, R.~S.~Lynch, M.~A. McLaughlin, N.~McMann, J.~Page, N.~T.~Palliyaguru, J.~D.~Romano, X.~Siemens, J.~K.~Swiggum, \textit{\textbf{S.~R.~Taylor}}, K.~Williamson \\ 
&& {\color{color1} \href{https://arxiv.org/abs/1907.07348}{Submitted to the Astronomy \& Astrophysics 2020 Decadal Survey (2019), arXiv:1907.07348}} \vspace{0.09cm}\\
\textbf{7.} & & ``\textit{The NANOGrav Program for Gravitational Waves and Fundamental Physics}'' \\ 
&& A.~Brazier, S.~Chatterjee, T.~Cohen, J.~M.~Cordes, M.~E.~DeCesar, P.~B.~Demorest, J.~S.~Hazboun, M.~T.~Lam, R.~S.~Lynch, M.~A. McLaughlin, S.~M.~Ransom, X.~Siemens, \textit{\textbf{S.~R.~Taylor}}, S.~J.~Vigeland \\ 
&& {\color{color1} \href{https://arxiv.org/abs/1908.05356}{Submitted to the Astronomy \& Astrophysics 2020 Decadal Survey (2019), arXiv:1908.05356}} \vspace{0.09cm}\\
\textbf{6.} & & ``\textit{Supermassive Black-hole Demographics \& Environments With Pulsar Timing Arrays}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}}, S.~Burke-Spolaor, P.~T.~Baker, M.~Charisi, K.~Islo, L.~Z.~Kelley, D.~R.~Madison, J.~Simon, S.~Vigeland \\ 
&& {\color{color1} \href{https://arxiv.org/abs/1903.08183}{Submitted to the Astronomy \& Astrophysics 2020 Decadal Survey (2019), arXiv:1903.08183}} \vspace{0.09cm}\\
\textbf{5.} & & ``\textit{Astro2020 Science White Paper: The Next Decade of Astroinformatics and Astrostatistics}'' \\ 
&& A.~Siemiginowska, G.~Eadie, I.~Czekala, [and 49 others, including \textit{\textbf{S.~R.~Taylor}}] \\ 
&& {\color{color1} \href{https://arxiv.org/abs/1903.06796}{Submitted to the Astronomy \& Astrophysics 2020 Decadal Survey (2019), arXiv:1903.06796}} \vspace{0.09cm}\\
\textbf{4.} & & ``\textit{From Megaparsecs To Milliparsecs: Galaxy Evolution \& Supermassive Black Holes with NANOGrav and the ngVLA}'' \\ 
&& \textit{\textbf{S.~R.~Taylor}} and J.~Simon \\ 
&& \href{http://ngvla.nrao.edu/page/scibook}{{\color{color1} Science With A Next-Generation Very Large Array [ngVLA science book] (2018)}} \vspace{0.09cm}\\
\textbf{3.} & & ``\textit{Solar System Ephemerides, Pulsar Timing, Gravitational Waves, \& Navigation}'' \\ 
&& T.~J.~W.~Lazio, S.~Bhaskaran, C.~Cutler, W.~M.~Folkner, R.~S.~Park, J.~A.~Ellis, T.~Ely, \textit{\textbf{S.~R.~Taylor}}, M.~Vallisneri \\ 
&& \href{https://doi.org/10.1017/S1743921317009711}{{\color{color1} Pulsar Astrophysics the Next Fifty Years, Proceedings of the International Astronomical Union, IAU Symposium, Volume 337, pp. 150-153 (2018)}} \vspace{0.09cm}\\
\textbf{2.} & & ``\textit{Summary of Session C1: pulsar timing arrays}'' \\ 
&& R.~M.~Shannon, S.~Chamberlin, N.~J.~Cornish, J.~A.~Ellis, C.~M.~F.~Mingarelli, D.~Perrodin, P.~Rosado, A.~Sesana, \textit{\textbf{S.~R.~Taylor}}, [and 14 others] \\ 
&& \href{http://link.springer.com/article/10.1007\%2Fs10714-014-1765-4}{{\color{color1} General Relativity and Gravitation, \textbf{46}:1765 (2014)}} \vspace{0.09cm}\\
\textbf{1.} & & ``\textit{Using Swarm Intelligence To Accelerate Pulsar Timing Analysis}'' \\ 
&& \textbf{S.~R.~Taylor}, J.~R.~Gair, L.~Lentati \\ 
&& \href{https://arxiv.org/abs/1210.3489}{{\color{color1} arXiv:1210.3489 (2012)}} \vspace{0.09cm}\\
\end{longtable}
}

\end{document}


