\documentclass[11pt,letterpaper,sans]{moderncv}

\usepackage{graphicx}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{textcomp}
\usepackage{units}
\usepackage{lineno}
\usepackage{rotating}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{comment}
\usepackage{xcolor}


\moderncvstyle{banking}                           
\moderncvcolor{blue}    

\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,bindingoffset=0cm]{geometry}
\setlength{\hintscolumnwidth}{3cm}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{lastpage}
\usepackage{mathabx}
\cfoot{{\color{gray} Page \thepage\ of \pageref{LastPage}}}


\def\prd{{Phys. Rev.} D}
\def\PRL{{Phys.Rev.} Lett}
\def\apjl{{Astrophys. J.} Lett}
\def\apj{{Astrophys. J.}}
\def\CQG{{Class. Quantum Grav.}}
\def\aaps{{A\&AS}}
\def\pasj{{PASJ}}
\def\mnras{{MNRAS}} 
\def\aapr{{A\&ARv}}
\def\aap{{A\&A}}
\def\na{{New Astronomy}}
\def\ptp{{Progress of Theoretical Physics}}
\def\apjs{{ApJS}}
\def\araa{{ARA\&A}}
\def\ssr{{Space Sci. Rev.}} 

\newcommand{\cvreference}[9]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
   \ifthenelse{\equal{#6}{}}{}{#6\newline}%
  \ifthenelse{\equal{#7}{}}{}{#7\newline}%
  \ifthenelse{\equal{#8}{}}{}{\emailsymbol~{\footnotesize \texttt{\emaillink[]{#8}}}\newline}
    \ifthenelse{\equal{#9}{}}{}{\phonesymbol~#9}}
 
%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Stephen} % Your first name
\familyname{Taylor} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{References}
\address{TAPIR Group, MC $350$-$17$, California Institute of Technology}{1200 E. California Blvd, Pasadena, CA 91125}
\vspace{15pt}\phone[mobile]{+1~(626)~689-5832}
\email{srtaylor@caltech.edu}
\homepage{stevertaylor.github.io}
\social[github]{stevertaylor}
\social[linkedin][linkedin.com/in/stephen-taylor-a8164787]{stephen-taylor $\;\;\bullet\;\;$ \today}

\lhead{{\color{gray} \fontsize{10}{22}\mdseries\upshape{Stephen~R.~Taylor}}}
\rhead{{\color{gray} \fontsize{10}{10}\mdseries\upshape{srtaylor@caltech.edu}}}

%\definecolor{color1}{HTML}{1f77b4}
%\hypersetup{urlcolor=color1,linkcolor=color1}

\begin{document}
\makecvtitle 

%----------------------------------------------------------------------------------------
%  REFERENCES
%----------------------------------------------------------------------------------------
\vspace{-30pt}
\section{} 
\vspace{15pt}
\begin{cvcolumns}
\cvcolumn{}{\cvreference{Dr~Jonathan~R.~Gair [\textit{PhD advisor}]}
    {Reader, School of Mathematics}
    {James Clerk Maxwell Building}
    {Peter Guthrie Tait Road}
    {University of Edinburgh}
    {Edinburgh UK, EH9 3FD}
    {}
    {J.Gair@ed.ac.uk}
    {+44 (0) 131 650 4899}
    }
\cvcolumn{}{\cvreference{Prof. Xavier Siemens}
    {}%{Chair, NANOGrav}
    {Director, NANOGrav Physics Frontier Center}
    {Associate Professor}
    {Department of Physics}
    {University of Wisconsin--Milwaukee}
    {Milwaukee,  WI 53201}
    {siemens@gravity.phys.uwm.edu}
    {+1 (414) 229 6439}
    }
   \end{cvcolumns}
 
\vspace{20pt}
\begin{cvcolumns}
\cvcolumn{}{\cvreference{Dr~Michele~Vallisneri}
    {Director's Fellow}
    {Jet Propulsion Laboratory}
    {California Institute of Technology}
    {4800 Oak Grove Drive}
    {Pasadena, CA 91109}
    {}
    {michele.vallisneri@jpl.nasa.gov}
    {+1 (818) 395 9073}
    }
    \cvcolumn{}{\cvreference{Prof. Alberto Vecchio}
    {Head of Group}
    {School of Physics \& Astronomy}
    {University of Birmingham}
    {Edgbaston}
    {Birmingham UK, B15 2TT}
    {}
    {av@star.sr.bham.ac.uk}
    {+44 (0) 1214 146447}
    }
    \end{cvcolumns}
    
\vspace{20pt}
\begin{cvcolumns}
\cvcolumn{}{\cvreference{Dr~T.~Joseph~W.~Lazio}
    {Chief Scientist}
    {Interplanetary Network Directorate}
    {Jet Propulsion Laboratory}
    {California Institute of Technology}
    {4800 Oak Grove Drive}
    {Pasadena, CA 91109}
    {Joseph.Lazio@jpl.nasa.gov}
    {+1 (818) 354 4198}
    }
    \cvcolumn{}{\cvreference{Prof.~Neil~J.~Cornish}
    {Professor of Physics}
    {eXtreme Gravity Institute}
    {Department of Physics}
    {Montana State University}
    {Bozeman, MT 59717}
    {}
    {ncornish@montana.edu}
    {+1 (406) 994 7986}
    }
    \end{cvcolumns}
    
\end{document}