\documentclass[11pt,letterpaper,sans]{moderncv}

\usepackage{graphicx}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{textcomp}
\usepackage{units}
\usepackage{lineno}
\usepackage{rotating}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{comment}
\usepackage{xcolor}
\usepackage[gen]{eurosym}


\moderncvstyle{banking}                           
\moderncvcolor{blue}    

\renewcommand{\familydefault}{\sfdefault}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,bindingoffset=0cm]{geometry}
\setlength{\hintscolumnwidth}{3cm}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{lastpage}
\usepackage{mathabx}
\cfoot{{\color{gray} Page \thepage\ of \pageref{LastPage}}}


\def\prd{{Phys. Rev.} D}
\def\PRL{{Phys.Rev.} Lett}
\def\apjl{{Astrophys. J.} Lett}
\def\apj{{Astrophys. J.}}
\def\CQG{{Class. Quantum Grav.}}
\def\aaps{{A\&AS}}
\def\pasj{{PASJ}}
\def\mnras{{MNRAS}} 
\def\aapr{{A\&ARv}}
\def\aap{{A\&A}}
\def\na{{New Astronomy}}
\def\ptp{{Progress of Theoretical Physics}}
\def\apjs{{ApJS}}
\def\araa{{ARA\&A}}
\def\ssr{{Space Sci. Rev.}} 

\newcommand{\cvreference}[9]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
   \ifthenelse{\equal{#6}{}}{}{#6\newline}%
  \ifthenelse{\equal{#7}{}}{}{#7\newline}%
  \ifthenelse{\equal{#8}{}}{}{\emailsymbol~{\footnotesize \texttt{\emaillink[]{#8}}}\newline}
    \ifthenelse{\equal{#9}{}}{}{\phonesymbol~#9}}
 
%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{\huge{Stephen~R.}} % Your first name
\familyname{\huge{Taylor}} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{\huge{Presentations}}
\address{Department of Physics \& Astronomy, Vanderbilt University}{6301 Stevenson Center, Nashville, TN 37235, USA}
\phone[mobile]{+1~(626)~689~5832}
\email{stephen.r.taylor@vanderbilt.edu}
\homepage{stevertaylor.github.io}
\social[github]{stevertaylor}
%\social[linkedin][linkedin.com/in/stephen-taylor-a8164787]{stephen-taylor $\;\;\bullet\;\;$ \today}
\social[linkedin][linkedin.com/in/stephen-taylor-a8164787]{stephen-taylor}

\lhead{{\color{gray} \fontsize{10}{22}\mdseries\upshape{Stephen~R.~Taylor}}}
\rhead{{\color{gray} \fontsize{10}{10}\mdseries\upshape{stephen.r.taylor@vanderbilt.edu}}}

%\definecolor{color1}{HTML}{1f77b4}
%\hypersetup{urlcolor=color1,linkcolor=color1}

\begin{document}
\makecvtitle 

%\vspace{-10mm}
%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

%\section{Full Publication List} %\vspace{-0.3cm} 

$\bullet$ \textbf{$91$ oral presentations (of which $54$ were invited), with $15$ conference leadership roles.}

%$\bullet$ Recent presentations are available to view at {\color{color1} \href{https://speakerdeck.com/stevertaylor}{https://speakerdeck.com/stevertaylor}}. \vspace{0.2cm}

$\bullet$ \textbf{Full list of presentations} given below, and at {\color{color1} \href{http://bit.ly/2xpZvrD}{http://bit.ly/2xpZvrD}}. \vspace{0.2cm}

\vspace{0.4cm}
\subsection{Invited talks} \vspace{-0.6cm}

\cvitem{}{\small
\hspace{-2cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
\textbf{54.} & & \textit{New Results From The Pulsar Timing Array Hunt For Nanohertz-frequency Gravitational Waves} \\
&& Joint DAA-DTP-InPTA Seminar (via Zoom), Tata Institute of Fundamental Research, \textbf{Mar 2021} \vspace{0.09cm}\\
\textbf{53.} & & \textit{New Results From The Pulsar Timing Array Hunt For Nanohertz-frequency Gravitational Waves} \\
&& Theoretical Astrophysics Seminar (via Zoom), University of Florida, \textbf{Mar 2021} \vspace{0.09cm}\\
\textbf{52.} & & \textit{New Results From The Pulsar Timing Array Hunt For Nanohertz-frequency Gravitational Waves} \\
&& Department of Physics \& Astronomy Colloquium (via Zoom), Western Kentucky University, \textbf{Feb 2021} \vspace{0.09cm}\\
\textbf{51.} & & \textit{New Results From The Pulsar Timing Array Hunt For Nanohertz-frequency Gravitational Waves} \\
&& Department of Physics Seminar (via Zoom), Southern Methodist University, \textbf{Nov 2020} \vspace{0.09cm}\\
\textbf{50.} & & \textit{New Results From The Pulsar Timing Array Hunt For Nanohertz-frequency Gravitational Waves} \\
&& Bahcall Lunch (via Zoom), Princeton University, \textbf{Oct 2020} \vspace{0.09cm}\\
\textbf{49.} & & \textit{New Results From The Pulsar Timing Array Hunt For Nanohertz-frequency Gravitational Waves} \\
&& SITP Seminar (via Zoom), Stanford University, \textbf{Oct 2020} \vspace{0.09cm}\\
\textbf{48.} & & \textit{New Results From The Pulsar Timing Array Hunt For Nanohertz-frequency Gravitational Waves} \\
&& Birmingham Astrophysics Seminar (via Zoom), University of Birmingham, Birmingham, UK, \textbf{Oct 2020} \vspace{0.09cm}\\
\textbf{47.} & & \textit{Charting The Next Frontier Of Gravitational Wave Astronomy With Pulsar Timing Arrays} \\
&& CIERA Astrophysics Seminar (via Zoom), CIERA, Northwestern University, \textbf{Sep 2020} \vspace{0.09cm}\\
\textbf{46.} & & \textit{Charting The Next Frontier Of Gravitational Wave Astronomy With Pulsar Timing Arrays} \\
&& Astrophysical and Cosmological Relativity Seminar (via Zoom), Albert Einstein Institute, Potsdam, Germany, \textbf{Jul 2020} \vspace{0.09cm}\\
\textbf{45.} & & \textit{Pulsar Timing Arrays: The Next Winow On The Warped Universe} \\
&& NSF QuarkNet Seminar (via Zoom), Vanderbilt University, Nashville TN, USA, \textbf{Jun 2020} \vspace{0.09cm}\\
\textbf{44.} & & \textit{Charting The Next Frontier Of Gravitational Wave Astronomy With Pulsar Timing Arrays} \\
&& Deutsche Forschungsgemeinshaft Research Training Group ``Models Of Gravity'' Colloquium (via Zoom), University of Bielefeld, Bielefeld, Germany, \textbf{Jun 2020} \vspace{0.09cm}\\
\textbf{43.} & & \textit{Charting The Next Frontier Of Nanohertz Gravitational Wave Astronomy With The International Pulsar Timing Array} \\
&& Invited seminar, l'Observatoire de Paris, Paris, France, \textbf{Dec 2019} \vspace{0.09cm}\\
\textbf{42.} & & \textit{Pulsar Timing Arrays: The Next Frontier of Gravitational Wave Astronomy} \\
&& Department of Physics Colloquium, Franklin \& Marshall College, Lancaster PA, USA, \textbf{Nov 2019} \vspace{0.09cm}\\
\textbf{41.} & & \textit{Pulsar Timing Arrays: The Next Frontier of Gravitational Wave Astronomy} \\
&& Astrophysics Division Seminar, NASA Goddard Space Flight Center, MD, USA, \textbf{Nov 2019} \vspace{0.09cm}\\
\textbf{40.} & & \textit{Supermassive Black Hole Demographics In The Era Of Multimessenger Pulsar Timing Array Detection} \\
&& Invited talk, SESAPS 2019 (South Eastern Section of the APS), Wilmington NC, USA, \textbf{Nov 2019} \vspace{0.09cm}\\
\textbf{39.} & & \textit{Pulsar Timing Arrays: The Next Frontier of Gravitational Wave Astronomy} \\
&& The Josephine Lawrence Hopkins Foundation Colloquium, Cornell University, Ithaca NY, USA, \textbf{Oct 2019} \vspace{0.09cm}\\
\textbf{38.} & & \textit{Pulsar Timing Arrays: The Next Frontier Of Gravitational Wave Astronomy} \\
&& Plenary presentation, 22nd International Conference on General Relativity and Gravitation (GR22) \& 13th Edoardo Amaldi Conference on Gravitational Waves (Amaldi13), Valencia, Spain, \textbf{Jul 2019} \vspace{0.09cm}\\
\textbf{37.} & & \textit{Solar System Ephemeris Noise} \\
&& OzGrav Pulsar Timing Workshop, Swinburne University of Technology, Melbourne, Australia, \textbf{May 2019} \vspace{0.09cm}\\
\textbf{36.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Department colloquium, Institute of Astronomy, University of Cambridge, Cambridge, UK, \textbf{Mar 2019} \vspace{0.09cm}\\
\textbf{35.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& CGCA Seminar, University of Wisconsin--Milwaukee, Milwaukee WI, USA, \textbf{Mar 2019} \vspace{0.09cm}\\
\textbf{34.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Invited seminar, Flatiron Center for Computational Astrophysics, New York NY, USA, \textbf{Feb 2019} \vspace{0.09cm}\\
\textbf{33.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Department of Physics \& Astronomy colloquium, University of Mississippi, Oxford MS, USA, \textbf{Feb 2019} \vspace{0.09cm}\\
\textbf{32.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Department of Physics \& Astronomy colloquium, Vanderbilt University, Nashville TN, USA, \textbf{Jan 2019} \vspace{0.09cm}\\
\textbf{31.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Department of Physics \& Astronomy colloquium, Carnegie Mellon University, Pittsburgh PA, USA, \textbf{Jan 2019} \vspace{0.09cm}\\
\textbf{30.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Department of Physics \& Astronomy colloquium, University of Minnesota, Minneapolis MN, USA, \textbf{Jan 2019} \vspace{0.09cm}\\
\textbf{29.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Department of Physics colloquium, University of Virginia, Charlottesville VA, USA, \textbf{Jan 2019} \vspace{0.09cm}\\
\textbf{28.} & & \textit{Supermassive Black-hole Demographics In The Era of Nanohertz Multi-messenger Astronomy} \\
&& American Astronomical Society, Seattle WA, USA, \textbf{Jan 2019} \vspace{0.09cm}\\
\textbf{27.} & & \textit{Compact Object Genealogy Across The Gravitational Wave Spectrum} \\
&& UVa+NRAO WUNA Lunch Talk, University of Virginia, Charlottesville VA, USA, \textbf{Oct 2018} \vspace{0.09cm}\\
\textbf{26.} & & \textit{Frontiers Of Pan-Spectral Gravitational-Wave Astrophysics} \\
&& Invited departmental seminar, Radboud University, Nijmegen, Netherlands, \textbf{Oct 2018} \vspace{0.09cm}\\
\textbf{25.} & & \textit{Compact Object Genealogy Across The Gravitational Wave Spectrum} \\
&& CGCA Seminar, University of Wisconsin--Milwaukee, Milwaukee WI, USA, \textbf{Sep 2018} \vspace{0.09cm}\\
\textbf{24.} & & \textit{Compact Object Genealogy Across The Gravitational Wave Spectrum} \\
&& USC Colloquium, University of Southern California, Los Angeles CA, USA, \textbf{Sep 2018} \vspace{0.09cm}\\
\textbf{23.} & & \textit{Compact Object Genealogy Across The Gravitational Wave Spectrum} \\
&& TAPIR Seminar, California Institute of Technology, Pasadena CA, USA, \textbf{Sep 2018} \vspace{0.09cm}\\
\textbf{22.} & & \textit{Nanohertz-frequency gravitational-wave astrophysics with pulsar-timing arrays} \\
&& COSPAR 2018, Pasadena CA, USA, \textbf{Jul 2018} \vspace{0.09cm}\\
\textbf{21.} & & \textit{Pulsar Timing Arrays: new advances toward detecting low-frequency gravitational waves} \\
&& American Physical Society, Columbus OH, USA, \textbf{Apr 2018} \vspace{0.09cm}\\
\textbf{20.} & & \textit{Beyond black holes with pulsar-timing arrays} \\
&& University of Virginia colloquium, Charlottesville VA, USA, \textbf{Mar 2018} \vspace{0.09cm}\\
\textbf{19.} & & \textit{Non-BH science with pulsar-timing arrays} \\
&& Black Holes Across The GW Spectrum, International Institute of Physics, Natal, Brazil, \textbf{Aug 2017} \vspace{0.09cm}\\
\textbf{18.} & & \textit{Bayesian inference for pulsar-timing arrays} \\
&& Black Holes Across The GW Spectrum, International Institute of Physics, Natal, Brazil, \textbf{Aug 2017} \vspace{0.09cm}\\
\textbf{17.} & & \textit{Supermassive black-hole binary astrophysics with pulsar-timing arrays} \\
&& Black Holes Across The GW Spectrum, International Institute of Physics, Natal, Brazil, \textbf{Aug 2017} \vspace{0.09cm}\\
\textbf{16.} & & \textit{Probing the nanohertz GW landscape with PTAs: a status report} \\
&& Gravitational Wave Physics \& Astronomy Workshop (GWPAW), Annecy, France, \textbf{May 2017} \vspace{0.09cm}\\
\textbf{15.} & & \textit{GW constraints on disc migration via pulsar timing} \\
&& The disc migration issue (Kavli workshop), Institute of Astronomy, Cambridge, UK, \textbf{May 2017} \vspace{0.09cm}\\
\textbf{14.} & & \textit{Constraining the physics of the final parsec of supermassive black-hole binary evolution} \\ 
&& Astronomy Colloquium, Swinburne University of Technology, Melbourne, Australia, \textbf{Feb 2017} \vspace{0.09cm}\\
\textbf{13.} & & \textit{Astrophysical inference of supermassive black-hole binaries with pulsar-timing arrays} \\ 
&& Leonard E. Parker Center seminar, University of Wisconsin--Milwaukee, Milwaukee WI, USA, \textbf{Oct 2016} \vspace{0.09cm}\\
\textbf{12.} & & \textit{Astrophysical inference of supermassive black-hole binaries with pulsar-timing arrays} \\ 
&& CIERA seminar, Northwestern University, Evanston IL, USA, \textbf{Oct 2016} \vspace{0.09cm}\\
\textbf{11.} & & \textit{New data-analysis approaches for gravitational-wave searches with pulsar-timing arrays} \\ 
&& Montana State University seminar, Bozeman MT, USA, \textbf{Oct 2016} \vspace{0.09cm}\\
\textbf{10.} & & \textit{New horizons in gravitational-wave astronomy with pulsar-timing arrays} \\ 
&& Armagh Observatory seminar, Armagh, UK, \textbf{Jul 2016} \vspace{0.09cm}\\
\textbf{9.} & & \textit{Probing the final-parsec problem with pulsar-timing arrays} \\ 
&& Anton Pannekoek Institutt seminar, University of Amsterdam, Amsterdam, Netherlands, \textbf{Jul 2016} \vspace{0.09cm}\\
\textbf{8.} & & \textit{Probing the final-parsec problem with pulsar-timing arrays} \\ 
&& Radboud University astrophysics seminar, Radboud, Netherlands, \textbf{Jul 2016} \vspace{0.09cm}\\
\textbf{7.} & & \textit{Gravitational-wave data-analysis techniques for pulsar-timing arrays} \\ 
&& IPTA conference, Stellenbosch, South Africa, \textbf{Jun 2016} \vspace{0.09cm}\\
\textbf{6.} & & \textit{Sources of nanohertz gravitational-waves for pulsar-timing array searches} \\ 
&& NANOGrav student workshop, Caltech, Pasadena CA, USA, \textbf{Mar 2016} \vspace{0.09cm}\\
\textbf{5.} & & \textit{Prospects for near future detection and astrophysical inference with PTAs} \\ 
&& Gravitational-wave group seminar, University of Birmingham, UK, \textbf{Dec 2015} \vspace{0.09cm}\\
\textbf{4.} & & \textit{Prospects for near future detection and astrophysical inference with PTAs} \\ 
&& Statistics group seminar (School of Mathematics), University of Edinburgh, UK, \textbf{Dec 2015} \vspace{0.09cm}\\
\textbf{3.} & & \textit{Prospects for near future detection and astrophysical inference with PTAs} \\ 
&& CaJAGWR seminar, California Institute of Technology, Pasadena, USA, \textbf{Dec 2015} \vspace{0.09cm}\\
\textbf{2.} & & \textit{Searching For Anisotropic Gravitational-wave Backgrounds Using Pulsar Timing Arrays} \\ 
&& Albert Einstein Institute (AEI) GW seminar, Hanover, Germany, \textbf{May 2013} \vspace{0.09cm}\\
\textbf{1.} & & \textit{Weighing the evidence for a gravitational-wave background} \\ 
&& Gravitational-wave group seminar, University of Birmingham, UK, \textbf{Dec 2012} 
\end{longtable}
}

%\vspace{-0.6cm}
\subsection{Contributed presentations} \vspace{-0.6cm}

\cvitem{}{\small
\hspace{-2cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
\textbf{37.} & & \textit{Mapping The Ultra Low-Frequency Gravitational-Wave Sky With A Network Of Pulsars} \\
&& 14th Amaldi Meeting (Virtual), \textbf{Jul 2021} \vspace{0.09cm}\\
\textbf{36.} & & \textit{Fast Bayesian GWB Amplitude Estimation Through Parallelized Methods} \\
&& IPTA Meeting (Virtual), \textbf{Jun 2021} \vspace{0.09cm}\\
\textbf{35.} & & \textit{Fast Bayesian GWB Amplitude Estimation Through Parallelized Methods} \\
&& NANOGrav Spring Meeting (Virtual), \textbf{May 2021} \vspace{0.09cm}\\
\textbf{34.} & & \textit{Mapping The Supermassive Binary Black-Hole Sky With Pulsar Timing Arrays} \\
&& AAS Winter Meeting (Virtual), \textbf{Jan 2021} \vspace{0.09cm}\\
\textbf{33.} & & \textit{Spatiotemporal Inference Strategies In The Quest For Gravitational Wave Detection With PTAs} \\
&& ICERM: Statistical Methods for the Detection, Classification, and Inference of Relativistic Objects (via Zoom), Brown University, \textbf{Nov 2020} \vspace{0.09cm}\\
\textbf{32.} & & \textit{The First 10 Years Of PTA Nanohertz GW Astronomy} \\
&& APS April Meeting (Virtual), \textbf{Apr 2020} \vspace{0.09cm}\\
\textbf{31.} & & \textit{Supermassive Black Hole Demographics In The Era Of Multimessenger Pulsar Timing Array Detection} \\
&& 30th Texas Symposium on Relativistic Astrophysics, Portsmouth, UK, \textbf{Dec 2019} \vspace{0.09cm}\\
\textbf{30.} & & \textit{From Bright Binaries To Bumpy Backgrounds: Mapping Realistic Gravitational Wave Skies With PTAs} \\
&& NANOGrav Fall Meeting, \textbf{Oct 2019} \vspace{0.09cm}\\
\textbf{29.} & & \textit{Constraining the environments \& progenitors of binary black holes across the gravitational-wave spectrum} \\ 
&& 12th International LISA Symposium, Chicago IL, \textbf{Jul 2018} \vspace{0.09cm}\\
\textbf{28.} & & \textit{The first 10 years of nanohertz gravitational-wave astronomy} \\ 
&& International Pulsar Timing Array meeting, Albuquerque NM, \textbf{Jun 2018} \vspace{0.09cm}\\
\textbf{27.} & & \textit{Progress updates in the NANOGrav gravitational-wave detection working group} \\ 
&& NANOGrav Spring 2018 meeting, University of Virginia, Charlottesville VA, \textbf{Mar 2018} \vspace{0.09cm}\\
\textbf{26.} & & \textit{The First Bayesian Solar-System Ephemeris} \\ 
&& NANOGrav Fall 2017 meeting, Lafayette College, Easton PA, \textbf{Nov 2017} \vspace{0.09cm}\\
\textbf{25.} & & \textit{GW constraints in the presence of solar-system ephemeris uncertainties} \\ 
&& International Pulsar Timing Array meeting, S\`evres, France, \textbf{Jul 2017} \vspace{0.09cm}\\
\textbf{24.} & & \textit{Solar-system ephemeris uncertainties \& GW constraints} \\ 
&& NANOGrav Spring meeting, West Virginia University, Morgantown WV, \textbf{Apr 2017} \vspace{0.09cm}\\
\textbf{23.} & & \textit{Modeling solar-system ephemeris uncertainties \& the impact on GW constraints} \\ 
&& EPTA meeting, Amsterdam, Netherlands, \textbf{Apr 2017} \vspace{0.09cm}\\
\textbf{22.} & & \textit{Bayesian model emulation of GW spectra for probes of the final parsec problem with pulsar-timing arrays} \\ 
&& American Astronomical Society meeting, Grapevine TX, USA, \textbf{Jan 2017} \vspace{0.09cm}\\
\textbf{21.} & & \textit{Bayesian model emulation of GW spectra for probes of the final parsec problem with pulsar-timing arrays} \\ 
&& American Physical Society April meeting, Washington DC, USA, \textbf{Jan 2017} \vspace{0.09cm}\\
\textbf{20.} & & \textit{Optimized gravitational-wave sky mapping with pulsar-timing arrays} \\ 
&& NANOGrav Fall Meeting 2016, NCSA, Urbana-Champaign IL, USA, \textbf{Oct 2016} \vspace{0.09cm}\\
\textbf{19.} & & \textit{Carrying the physics of supermassive black-hole binary evolution into pulsar-timing array searches} \\ 
&& EPTA meeting, Bielefeld, Germany, \textbf{May 2016} \vspace{0.09cm}\\
\textbf{18.} & & \textit{Are we there yet? Time to detection of nanohertz gravitational waves} \\ 
&& American Physical Society meeting, Salt Lake City UT, USA, \textbf{Apr 2016} \vspace{0.09cm}\\
\textbf{17.} & & \textit{Carrying the physics of supermassive black-hole binary evolution into pulsar-timing array searches} \\ 
&& NANOGrav meeting, Caltech, Pasadena CA, USA, \textbf{Mar 2016} \vspace{0.09cm}\\
\textbf{16.} & & \textit{Are we there yet? Time to detection of nanohertz gravitational waves} \\ 
&& NANOGrav meeting, McGill University, Montreal, Canada, \textbf{Oct 2015} \vspace{0.09cm}\\
\textbf{15.} & & \textit{Eccentric supermassive black-hole binary signals in pulsar-timing data} \\ 
&& European Pulsar Timing Array meeting, Bonn, Germany, \textbf{Jun 2015} \vspace{0.09cm}\\
\textbf{14.} & & \textit{Eccentric supermassive black-hole binary signals in pulsar-timing data} \\ 
&& American Physical Society meeting, Baltimore MD, USA, \textbf{Apr 2015} \vspace{0.09cm}\\
\textbf{13.} & & \textit{Eccentric supermassive black-hole binary signals in pulsar-timing data} \\ 
&& NANOGrav meeting, Arecibo, Puerto Rico, \textbf{Feb 2015} \vspace{0.09cm}\\
\textbf{12.} & & \textit{Exploring the cosmos with gravitational waves} \\ 
&& American Astronomical Society meeting, Seattle WA, USA, \textbf{Jan 2015} \vspace{0.09cm}\\
\textbf{11.} & & \textit{EPTA constraints on gravitational-wave anisotropy} \\ 
&& European Pulsar Timing Array meeting, Cambridge, UK, \textbf{Nov 2014} \vspace{0.09cm}\\
\textbf{10.} & & \textit{EPTA and IPTA searches for gravitational-wave background anisotropy} \\ 
&& International Pulsar Timing Array meeting, Banff, Canada, \textbf{Jun 2014} \vspace{0.09cm}\\
\textbf{9.} & & \textit{EPTA limits on gravitational-wave anisotropy} \\ 
&& European Pulsar Timing Array meeting, Astron, Netherlands, \textbf{May 2014} \vspace{0.09cm}\\
\textbf{8.} & & \textit{The pulsar-term in PTA continuous-wave searches: a blessing and a curse} \\ 
&& European Pulsar Timing Array meeting, Pula, Sardinia, \textbf{Oct 2013} \vspace{0.09cm}\\
\textbf{7.} & & \textit{Probing anisotropy of the GW background with pulsar timing arrays} \\ 
&& 20th International Conference on GR and Gravitation, 10th Amaldi Conference on GWs, Warsaw, \textbf{Jul 2013} \vspace{0.09cm}\\
\textbf{6.} & & \textit{The first PTA search pipeline for anisotropy in the GW background} \\ 
&& International Pulsar Timing Array meeting, Krabi, Thailand, \textbf{Jun 2013} \vspace{0.09cm}\\
\textbf{5.} & & \textit{Searching For Anisotropic Gravitational-wave Backgrounds Using Pulsar Timing Arrays} \\ 
&& European Pulsar Timing Array meeting, l'Observatoire de Paris, Paris, France, \textbf{Apr 2013} \vspace{0.09cm}\\
\textbf{4.} & & \textit{Weighing the evidence for a gravitational-wave background} \\ 
&& Institute of Astronomy seminar, University of Cambridge, UK, \textbf{Feb 2013} \vspace{0.09cm}\\
\textbf{3.} & & \textit{Weighing the evidence for a gravitational-wave background} \\ 
&& European Pulsar Timing Array meeting, Albert Einstein Institute (AEI), Potsdam, Germany, \textbf{Nov 2012} \vspace{0.09cm}\\
\textbf{2.} & & \textit{Milestones in Spacetime: Double Neutron-Star Binaries as Gravitational-Wave Standard Sirens} \\ 
&& Institute of Astronomy seminar, University of Cambridge, UK, \textbf{Jun 2012} \vspace{0.09cm}\\
\textbf{1.} & & \textit{Hubble without the Hubble: Cosmology using advanced gravitational-wave detectors alone} \\ 
&& Gravitational-Wave Meeting, Institut de Ci\`encies de l'Espai, Barcelona, Spain, \textbf{Feb 2012} 
\end{longtable}
}

%\vspace{-0.6cm}
\subsection{Posters}\vspace{-0.6cm}

\cvitem{}{\small
\hspace{-2cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
\textbf{5.} & & \textit{The NANOGrav 11-year Dataset: Pulsar Timing Constraints On The Stochastic GW Background} \\ 
&& American Astronomical Society Meeting, Seattle WA, \textbf{Jan 2019} \vspace{0.09cm}\\
\textbf{4.} & & \textit{The Black Hole Zoo: Populations, Pathways, \& Origins} \\ 
&& Gravitational Wave Physics \& Astronomy Meeting, Washington DC, \textbf{Dec 2018} \vspace{0.09cm}\\
\textbf{3.} & & \textit{Galactic environment effects on gravitational wave signals in pulsar timing arrays} \\ 
&& Postdoc Research Day, NASA Jet Propulsion Laboratory, \textbf{Aug 2015} \vspace{0.09cm}\\
\textbf{2.} & & \textit{Cosmology without EM counterparts: Standard sirens in the advanced era and beyond} \\ 
&& Rattle and Shine, KITP Santa Barbara, USA, \textbf{Aug 2012} \vspace{0.09cm}\\
\textbf{1.} & & \textit{Cosmology using advanced gravitational-wave detectors alone} \\ 
&& Graduate Student Conference 2011, Cavendish Laboratory, University of Cambridge, UK, \textbf{Dec 2011} \vspace{0.09cm}\\
\end{longtable}
}

\end{document}