%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\def\prd{{Phys. Rev.} D}
\def\PRL{{Phys.Rev.} Lett}
\def\apjl{{Astrophys. J.} Lett}
\def\apj{{Astrophys. J.}}
\def\CQG{{Class. Quantum Grav.}}
\def\aaps{{A\&AS}}
\def\pasj{{PASJ}}
\def\mnras{{MNRAS}} 
\def\aapr{{A\&ARv}}
\def\aap{{A\&A}}
\def\na{{New Astronomy}}
\def\ptp{{Progress of Theoretical Physics}}
\def\apjs{{ApJS}}
\def\araa{{ARA\&A}}
\def\ssr{{Space Sci. Rev.}} 

\usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
\makeatletter
\newcommand*{\emailA}[1]{\def\@emailA{#1}}
\newcommand*{\emailB}[1]{\def\@emailB{#1}}
\patchcmd{\maketitle}% <cmd>
  {\ifthenelse{\isundefined{\@email}}{}{\addtomaketitle{\emailsymbol\emaillink{\@email}}}}% <search>
  {\ifthenelse{\isundefined{\@emailA}}{}{\addtomaketitle{\emailsymbol\emaillink{\@emailA}}}%
   \ifthenelse{\isundefined{\@emailB}}{}{\addtomaketitle{\emailsymbol\emaillink{\@emailB}}}}% <replace>
  {}{}% <success><failure>
\makeatother
 
%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Stephen} % Your first name
\familyname{Taylor} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Jet Propulsion Laboratory, 4800 Oak Grove Drive}{Pasadena, CA 91109}
\phone[mobile]{+1 (626) 689-5832}
\emailA{Stephen.R.Taylor@jpl.nasa.gov}
\emailB{steve.taylor1987@gmail.com}
\homepage{stevertaylor.github.io}
\social[github]{stevertaylor}
\social[linkedin][linkedin.com/in/stephen-taylor-a8164787]{stephen-taylor}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional experience}

\cventry{2014--Present}{NASA Postdoctoral Fellow}{\textsc{NASA Jet Propulsion Laboratory}}{Pasadena, USA}{}{}
\cventry{2014--Present}{Visting scholar (TAPIR group)}{\textsc{California Institute of Technology}}{Pasadena, USA}{}{}
\cventry{2010--2014}{PhD candidate}{\textsc{Institute of Astronomy, University of Cambridge}}{Cambridge, UK}{}{}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2010--2014}{PhD (Astronomy)}{Institute of Astronomy, University of Cambridge}{Cambridge, UK}{}{}  
\cventry{2006--2010}{MPhys}{University of Oxford}{Oxford, UK}{First Class}{Graduated $1^\mathrm{st}$ in Jesus College, $4^\mathrm{th}$ across University}

%----------------------------------------------------------------------------------------
%   THESIS
%----------------------------------------------------------------------------------------

\section{Doctoral Thesis}

\cvitem{Title}{\emph{Exploring the cosmos with gravitational waves}}
\cvitem{Supervisor}{Dr. Jonathan R. Gair}
\cvitem{Description}{A new Bayesian hierarchical modelling scheme is introduced to use compact-binary gravitational-wave standard sirens to infer the mass-distribution of the binary population, the progenitor star-formation rate, and cosmological parameters. Advanced pulsar-timing array techniques are developed to map the nanohertz gravitational-wave sky through a parametrized overlap-reduction function, and large accelerations to the Bayesian inference of single supermassive black-hole binary searches are proposed.}

\section{Grants \& Funding}

\cvitem{``New Directions and New Opportunities for NANOGrav Astrophysics''}{Awarded $\$11$k for a proposal on behalf of the Astrophysics Working Group of NANOGrav. Funding will ensure undergraduate/graduate students and outside experts can attend a sprint week in March 2017 to advance several key areas of interest, and to achieve rapid progress on collaboration projects.}

%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards \& Prizes}

\cvitem{2015}{International Pulsar Timing Array (IPTA) Steering Committee Prize --- ``Honourable Mention"}
\cvitem{2015}{Gravitational Wave International Committee (GWIC) Thesis Prize --- ``Honourable Mention"}
\cvitem{2014}{NASA Postdoctoral Fellowship (JPL)}
\cvitem{2014}{Royal Astronomical Society Travel Award --- $\pounds 750$}\cvitem{2013}{Royal Astronomical Society Travel Award --- $\pounds 700$}\cvitem{2012--2014}{Christ's College (Cambridge) Travel Grants [various; total exceeds $\pounds 1$k]}
\cvitem{2010}{Science and Technology Facilities Council (STFC) --- full PhD studentship award}
\cvitem{2008}{Examiner's Prize, Oxford Physics Speaking Competition}
\cvitem{2007}{Oxford Physics department prize for laboratory work}
\cvitem{2007--2010}{Undergraduate Scholar of Jesus College, Oxford}
\cvitem{2006--2010}{Regularly awarded Oxford undergraduate departmental and college examination prizes}

%----------------------------------------------------------------------------------------
%   TEACHING SECTION
%----------------------------------------------------------------------------------------

\section{Teaching experience}

\cvitem{Jun--Aug 2016}{Co-supervisor of Caltech summer undergraduate student}
\cvitem{May 2016}{Lecturer for Caltech's TAPIR gravitational-wave class}
\cvitem{Mar 2016}{Co-organizer of student workshop at NANOGrav Spring meeting}
\cvitem{Sep 2015}{Lecturer for NANOGrav detection-group workshop at Caltech}
\cvitem{Jun 2015}{Lecturer at ``CSI PTA'' Aspen summer workshop}
\cvitem{2011--2013}{Supervisor for Cambridge Part II undergraduate students in \textsc{Relativity}}
\cvitem{2011}{Prepared computing coursework for Cambridge Part II undergraduate students}

%----------------------------------------------------------------------------------------
%   OUTREACH SECTION
%----------------------------------------------------------------------------------------

\section{Outreach}

\cvitem{2016}{Featured gravitational-wave expert at NASA's``Ticket to Explore JPL'' event}
\cvitem{2013}{Presentation at Cambridge's Institute of Astronomy Open Day}
\cvitem{2012--2014}{Presentation to prospective students (Institute of Astronomy graduate interviews)}
\cvitem{2012}{Outreach talk at Institute of Astronomy public-observing evening}
\cvitem{2011}{Presentation at Cambridge's Institute of Astronomy Open Day}

%----------------------------------------------------------------------------------------
%   AFFILIATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Professional affiliations}

\cvitem{North American Nanohertz Observatory for Gravitational-waves (NANOGrav)}{Full member}
\cvitem{European Pulsar Timing Array (EPTA)}{Member}
\cvitem{International Pulsar Timing Array (IPTA)}{Member}
\cvitem{American Physical Society (and DGRAV)}{Member}
\cvitem{American Astronomical Society}{Member}
\cvitem{Royal Astronomical Society}{Fellow}

%----------------------------------------------------------------------------------------
%   PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------

\subsection{Publications in international peer-reviewed journals}
\cvitem{May 2016}{G.~Desvignes, R.~N.~Caballero, L.~Lentati, [and 40 others, including \textit{\textbf{S.~R.~Taylor}}]. ``\textit{High-precision timing of 42 millisecond pulsars with the European Pulsar Timing Array}''. MNRAS, 458:3341--3380.}\cvitem{May 2016}{L.~Lentati, R.~M.~Shannon, W.~A.~Coles, [and 80 others, including \textit{\textbf{S.~R.~Taylor}}]. ``\textit{From spin noise to systematics: stochastic processes in the first International Pulsar Timing Array data release}''. MNRAS, 458:2161--2187.}\cvitem{May 2016 }{J.~P.~W.~Verbiest, L.~Lentati, G.~Hobbs, [and 89 others, including \textit{\textbf{S.~R.~Taylor}}]. ``\textit{The International Pulsar Timing Array: First data release}''. MNRAS, 458:1267--1288.}\cvitem{Apr 2016 }{Z.~Arzoumanian, A.~Brazier, S.~Burke-Spolaor, [and 48 others, including \textit{\textbf{S.~R.~Taylor}}]. ``\textit{The NANOGrav Nine-year Data Set: Limits on the Isotropic Stochastic Gravitational Wave Background}''. Astrophys. J., 821:13.}\cvitem{Apr 2016 }{R.~N.~Caballero, K.~J.~Lee, L.~Lentati, [and 36 others, including \textit{\textbf{S.~R.~Taylor}}]. ``\textit{The noise properties of 42 millisecond pulsars from the European Pulsar Timing Array and their impact on gravitational-wave searches}''. MNRAS, 457:4421--4440.}\cvitem{Mar 2016 }{\textit{\textbf{S.~R.~Taylor}}, M.~Vallisneri, J.~A.~Ellis, C.~M.~F.~Mingarelli, T.~J.~W.~Lazio, and R.~van Haasteren. ``\textit{Are We There Yet? Time to Detection of Nanohertz Gravitational  Waves Based on Pulsar-timing Array Limits}''. Astrophys. J. Lett, 819:L6.}\cvitem{Jan 2016 }{\textit{\textbf{S.~R.~Taylor}}, E.~A.~Huerta, J.~R.~Gair, and S.~T.~McWilliams. ``\textit{Detecting Eccentric Supermassive Black Hole Binaries with Pulsar Timing Arrays: Resolvable Source Strategies}''. Astrophys. J., 817:70.}\cvitem{Jan 2016 }{S.~Babak, A.~Petiteau, A.~Sesana, P.~Brem, P.~A.~Rosado, \textit{\textbf{S.~R.~Taylor}}, [and 30 others]. ``\textit{European Pulsar Timing Array limits on continuous gravitational waves from individual supermassive black hole binaries}''. MNRAS, 455:1665--1679.}\cvitem{Nov 2015 }{J.~R.~Gair, J.~D.~Romano, and \textit{\textbf{S.~R.~Taylor}}. ``\textit{Mapping gravitational-wave backgrounds of arbitrary polarisation using pulsar timing arrays}''. Phys. Rev. D, 92(10):102003.}\cvitem{Nov 2015 }{L.~Lentati, \textit{\textbf{S.~R.~Taylor}}, C.~M.~F.~Mingarelli, [and 33 others]. ``\textit{European Pulsar Timing Array limits on an isotropic stochastic gravitational-wave background}''. MNRAS, 453:2576--2598.}\cvitem{Sep 2015 }{E.~A.~Huerta, S.~T.~McWilliams, J.~R.~Gair, and \textit{\textbf{S.~R.~Taylor}}. ``\textit{Detection of eccentric supermassive black hole binaries with pulsar timing arrays: Signal-to-noise ratio calculations}''. Phys. Rev. D, 92(6):063010.}\cvitem{Aug 2015 }{J.~D.~Romano, \textit{\textbf{S.~R.~Taylor}}, N.~J.~Cornish, J.~Gair, C.~M.~F.~Mingarelli, and R.~van Haasteren. ``\textit{Phase-coherent mapping of gravitational-wave backgrounds using ground-based laser interferometers}'', Phys. Rev. D, 92(4):042003.}\cvitem{Jul 2015}{\textit{\textbf{S.~R.~Taylor}}, C.~M.~F.~Mingarelli, J.~R.~Gair, [and 32 others]. ``\textit{Limits on Anisotropy in the Nanohertz Stochastic Gravitational Wave Background}''. Phys.Rev. Lett, 115(4):041101.}\cvitem{Mar 2015}{C.~J.~Moore, \textit{\textbf{S.~R.~Taylor}}, and J.~R.~Gair. ``\textit{Estimating the sensitivity of pulsar timing arrays}'', Classical and Quantum Gravity, 32(5):055004.}\cvitem{Nov 2014}{\textit{\textbf{S.~R.~Taylor}}, J.~Ellis, and J.~Gair. ``\textit{Accelerated Bayesian model-selection and parameter-estimation in continuous gravitational-wave searches with pulsar-timing arrays}''. Phys. Rev. D, 90(10):104028.}\cvitem{Oct 2014}{J.~Gair, J.~D.~Romano, \textit{\textbf{S.~R.~Taylor}}, and C.~M.~F.~Mingarelli. ``\textit{Mapping gravitational-wave backgrounds using methods from CMB analysis: Application to pulsar timing arrays}''. Phys. Rev. D, 90(8):082001.}\cvitem{Aug 2014}{R.~M.~Shannon, S.~Chamberlin, N.~J.~Cornish, J.~A.~Ellis, C.~M.~F.~Mingarelli, D.~Perrodin, P.~Rosado, A.~Sesana, \textit{\textbf{S.~R.~Taylor}}, [and 14 others]. ``\textit{Summary of Session C1: pulsar timing arrays}''. General Relativity and Gravitation, 46:1765.}\cvitem{Oct 2013}{\textit{\textbf{S.~R.~Taylor}} and J.~R.~Gair. ``\textit{Searching for anisotropic gravitational-wave backgrounds using pulsar timing arrays}''. Phys. Rev. D, 88(8):084001.}\cvitem{May 2013}{L.~Lentati, P.~Alexander, M.~P.~Hobson, \textit{\textbf{S.~R.~Taylor}}, J.~Gair, S.~T.~Balan, and R.~van Haasteren. ``\textit{Hyper-efficient model-independent Bayesian method for the analysis  of  pulsar timing data}''. Phys. Rev. D, 87(10):104021.}\cvitem{Feb 2013 }{\textit{\textbf{S.~R.~Taylor}}, J.~R.~Gair, and L.~Lentati. ``\textit{Weighing the evidence for a gravitational-wave background in the first International Pulsar Timing Array data challenge}''. Phys. Rev. D, 87(4):044035.}\cvitem{Jul 2012}{\textit{\textbf{S.~R.~Taylor}} and J.~R.~Gair. ``\textit{Cosmology with the lights off: Standard sirens in the Einstein Telescope era}''. Phys. Rev. D, 86(2):023502.}\cvitem{Jan 2012}{\textit{\textbf{S.~R.~Taylor}}, J.~R.~Gair, and I.~Mandel. ``\textit{Cosmology using advanced gravitational-wave detectors alone}''. Phys. Rev. D, 85(2):023535.}


\section{Recent presentations}

\subsection{Invited talks}
\cvitem{Jun 2016}{\textit{Gravitational-wave data-analysis techniques for pulsar-timing arrays}, IPTA conference, Stellenbosch, South Africa}
\cvitem{Apr 2016}{\textit{Sources of nanohertz gravitational-waves for pulsar-timing array searches}, NANOGrav student workshop, California Institute of Technology, Pasadena CA, USA}

\subsection{Contributed talks}
\cvitem{May 2016}{\textit{Carrying the physics of supermassive black-hole binary evolution into pulsar-timing array searches}, EPTA meeting, Bielefeld, Germany}
\cvitem{Apr 2016}{\textit{Are we there yet? Time to detection of nanohertz gravitational waves}, American Physical Society meeting, Salt Lake City UT, USA}
\cvitem{Mar 2016}{\textit{Carrying the physics of supermassive black-hole binary evolution into pulsar-timing array searches}, NANOGrav meeting, California Institute of Technology, Pasadena CA, USA}
\cvitem{Oct 2015}{\textit{Are we there yet? Time to detection of nanohertz gravitational waves}, NANOGrav meeting, McGill University, Montreal, Canada}
\cvitem{Jun 2015}{\textit{Eccentric supermassive black-hole binary signals in pulsar-timing data}, European Pulsar Timing Array meeting, Bonn, Germany}
\cvitem{Apr 2015}{\textit{Eccentric supermassive black-hole binary signals in pulsar-timing data}, American Physical Society meeting, Baltimore MD, USA}
\cvitem{Feb 2015}{\textit{Eccentric supermassive black-hole binary signals in pulsar-timing data}, NANOGrav meeting, Arecibo, Puerto Rico}
\cvitem{Jan 2015}{\textit{Exploring the cosmos with gravitational waves}, American Astronomical Society meeting, Seattle WA, USA}
\cvitem{Nov 2014}{\textit{EPTA constraints on gravitational-wave anisotropy}, European Pulsar Timing Array meeting, Cambridge, UK}
\cvitem{Jun 2014}{\textit{EPTA and IPTA searches for gravitational-wave background anisotropy}, International Pulsar Timing Array meeting, Banff, Canada}
\cvitem{May 2014}{\textit{EPTA limits on gravitational-wave anisotropy}, European Pulsar Timing Array meeting, Astron, Netherlands}
\cvitem{Jun 2014}{\textit{EPTA and IPTA searches for gravitational-wave background anisotropy}, International Pulsar Timing Array meeting, Banff, Canada}
\cvitem{Oct 2013}{\textit{The pulsar-term in PTA continuous-wave searches: a blessing and a curse}, European Pulsar Timing Array meeting, Pula, Sardinia}
\cvitem{Jul 2013}{\textit{Probing anisotropy of the GW background with pulsar timing arrays}, 20th International Conference on General Relativity and Gravitation and 10th Amaldi Conference on Gravitational Waves, Warsaw}
\cvitem{Jun 2013}{\textit{The first PTA search pipeline for anisotropy in the GW background}, International Pulsar Timing Array meeting, Krabi, Thailand}
\cvitem{Apr 2013}{\textit{Searching For Anisotropic Gravitational-wave Backgrounds Using Pulsar Timing Arrays}, European Pulsar Timing Array meeting, l'Observatoire de Paris, Paris}
\cvitem{Nov 2012}{\textit{Weighing the evidence for a gravitational-wave background}, European Pulsar Timing Array meeting, Albert Einstein Institute (AEI), Potsdam}
\cvitem{Feb 2012}{\textit{Hubble without the Hubble: Cosmology using advanced gravitational-wave detectors alone}, Gravitational-Wave Meeting, Institut de Ciències de l'Espai, Barcelona}

\subsection{Seminars}
\cvitem{Dec 2015}{\textit{Prospects for near future detection and astrophysical inference with PTAs}, Gravitational-wave group seminar, University of Birmingham, UK}
\cvitem{Dec 2015}{\textit{Prospects for near future detection and astrophysical inference with PTAs}, Statistics group seminar (School of Mathematics), University of Edinburgh, UK}
\cvitem{Dec 2015}{\textit{Prospects for near future detection and astrophysical inference with PTAs}, CaJAGWR seminar, California Institute of Technology}
\cvitem{May 2013}{\textit{Searching For Anisotropic Gravitational-wave Backgrounds Using Pulsar Timing Arrays}, Albert Einstein Institute (AEI), Hanover}
\cvitem{Feb 2013}{\textit{Weighing the evidence for a gravitational-wave background, Institute of Astronomy seminar}, University of Cambridge}
\cvitem{Dec 2012}{\textit{Weighing the evidence for a gravitational-Wave background}, University of Birmingham}
\cvitem{Jun 2012}{\textit{Milestones in Spacetime: Double Neutron-Star Binaries as Gravitational-Wave Standard Sirens}, Institute of Astronomy seminar, University of Cambridge}

\subsection{Posters}
\cvitem{Aug 2015}{\textit{Galactic environment effects on gravitational wave signals in pulsar timing arrays}, Postdoc Research Day, NASA Jet Propulsion Laboratory}
\cvitem{Aug 2012}{\textit{Cosmology without EM counterparts: Standard sirens in the advanced era and beyond}, Rattle and Shine, KITP Santa Barbara}
\cvitem{Dec 2011}{\textit{Cosmology using advanced gravitational-wave detectors alone}, Graduate Student Conference 2011, Cavendish Laboratory, University of Cambridge}

%----------------------------------------------------------------------------------------
%   PUBLICATIONS
%----------------------------------------------------------------------------------------

%\nocite{*}
%\bibliographystyle{plainyr-rev}
%\bibliography{staylor_cv}   

%\nocite{*}
%\begin{thebibliography}{10}
%
%\bibitem{tve+16}
%\textbf{{Taylor}, S.~R.}, L.~Lentati, S.~Babak, P.~Brem, J.~R.~Gair, A.~Sesana, A.~Vecchio.
%\newblock {\emph{``All correlations must die: Assessing the significance of a stochastic gravitational-wave signals in pulsar-timing arrays"}}.
%\newblock {\emph{in prep.}}, June 2016.
%
%\bibitem{tve+16}
%\textbf{{Taylor}, S.~R.}, M.~{Vallisneri}, J.~A. {Ellis}, C.~M.~F.
%  {Mingarelli}, T.~J.~W. {Lazio}, and R.~{van Haasteren}.
%\newblock {\emph{``Are We There Yet? Time to Detection of Nanohertz Gravitational Waves
%  Based on Pulsar-timing Array Limits"}}.
%\newblock {\emph \apjl}, 819:L6, March 2016.
%
%\bibitem{thgm16}
%\textbf{{Taylor}, S.~R.}, E.~A. {Huerta}, J.~R. {Gair}, and S.~T. {McWilliams}.
%\newblock {\emph{``Detecting Eccentric Supermassive Black Hole Binaries with Pulsar
%  Timing Arrays: Resolvable Source Strategies"}}.
%\newblock {\emph \apj}, 817:70, January 2016.
%
%\bibitem{tmg+15}
%\textbf{{Taylor}, S.~R.}, C.~M.~F. {Mingarelli}, J.~R. {Gair}, A.~{Sesana},
%  G.~{Theureau}, S.~{Babak}, C.~G. {Bassa}, P.~{Brem}, M.~{Burgay}, R.~N.
%  {Caballero}, D.~J. {Champion}, I.~{Cognard}, G.~{Desvignes}, L.~{Guillemot},
%  J.~W.~T. {Hessels}, G.~H. {Janssen}, R.~{Karuppusamy}, M.~{Kramer},
%  A.~{Lassus}, P.~{Lazarus}, L.~{Lentati}, K.~{Liu}, S.~{Os{\l}owski},
%  D.~{Perrodin}, A.~{Petiteau}, A.~{Possenti}, M.~B. {Purver}, P.~A. {Rosado},
%  S.~A. {Sanidas}, R.~{Smits}, B.~{Stappers}, C.~{Tiburzi}, R.~{van Haasteren},
%  A.~{Vecchio}, J.~P.~W. {Verbiest}, and {EPTA Collaboration}.
%\newblock {\emph{``Limits on Anisotropy in the Nanohertz Stochastic Gravitational Wave
%  Background"}}.
%\newblock {\emph \PRL}, 115(4):041101, July 2015.
%
%\bibitem{teg14}
%\textbf{{Taylor}, S.}, J.~{Ellis}, and J.~{Gair}.
%\newblock {\emph{``Accelerated Bayesian model-selection and parameter-estimation in
%  continuous gravitational-wave searches with pulsar-timing arrays"}}.
%\newblock {\emph \prd}, 90(10):104028, November 2014.
%
%\bibitem{tg13}
%\textbf{{Taylor}, S.~R.} and J.~R. {Gair}.
%\newblock {\emph{``Searching for anisotropic gravitational-wave backgrounds using
%  pulsar timing arrays"}}.
%\newblock {\emph \prd}, 88(8):084001, October 2013.
%
%\bibitem{tgl13}
%\textbf{{Taylor}, S.~R.}, J.~R. {Gair}, and L.~{Lentati}.
%\newblock {\emph{``Weighing the evidence for a gravitational-wave background in the
%  first International Pulsar Timing Array data challenge"}}.
%\newblock {\emph \prd}, 87(4):044035, February 2013.
%
%\bibitem{tg12}
%\textbf{{Taylor}, S.~R.} and J.~R. {Gair}.
%\newblock {\emph{``Cosmology with the lights off: Standard sirens in the Einstein
%  Telescope era"}}.
%\newblock {\emph \prd}, 86(2):023502, July 2012.
%
%\bibitem{tgm12}
%\textbf{{Taylor}, S.~R.}, J.~R. {Gair}, and I.~{Mandel}.
%\newblock {\emph{``Cosmology using advanced gravitational-wave detectors alone"}}.
%\newblock {\emph \prd}, 85(2):023535, January 2012.
%
%\bibitem{dcl+16}
%G.~{Desvignes}, R.~N. {Caballero}, L.~{Lentati}, J.~P.~W. {Verbiest}, D.~J.
%  {Champion}, B.~W. {Stappers}, G.~H. {Janssen}, P.~{Lazarus},
%  S.~{Os{\l}owski}, S.~{Babak}, C.~G. {Bassa}, P.~{Brem}, M.~{Burgay},
%  I.~{Cognard}, J.~R. {Gair}, E.~{Graikou}, L.~{Guillemot}, J.~W.~T. {Hessels},
%  A.~{Jessner}, C.~{Jordan}, R.~{Karuppusamy}, M.~{Kramer}, A.~{Lassus},
%  K.~{Lazaridis}, K.~J. {Lee}, K.~{Liu}, A.~G. {Lyne}, J.~{McKee}, C.~M.~F.
%  {Mingarelli}, D.~{Perrodin}, A.~{Petiteau}, A.~{Possenti}, M.~B. {Purver},
%  P.~A. {Rosado}, S.~{Sanidas}, A.~{Sesana}, G.~{Shaifullah}, R.~{Smits},
%  \textbf{{Taylor}, S.~R.}, G.~{Theureau}, C.~{Tiburzi}, R.~{van Haasteren},
%  and A.~{Vecchio}.
%\newblock {\emph{``High-precision timing of 42 millisecond pulsars with the European
%  Pulsar Timing Array"}}.
%\newblock {\emph \mnras}, 458:3341--3380, May 2016.
%
%\bibitem{ls+16}
%L.~{Lentati}, R.~M. {Shannon}, W.~A. {Coles}, J.~P.~W. {Verbiest}, R.~{van
%  Haasteren}, J.~A. {Ellis}, R.~N. {Caballero}, R.~N. {Manchester},
%  Z.~{Arzoumanian}, S.~{Babak}, C.~G. {Bassa}, N.~D.~R. {Bhat}, P.~{Brem},
%  M.~{Burgay}, S.~{Burke-Spolaor}, D.~{Champion}, S.~{Chatterjee},
%  I.~{Cognard}, J.~M. {Cordes}, S.~{Dai}, P.~{Demorest}, G.~{Desvignes},
%  T.~{Dolch}, R.~D. {Ferdman}, E.~{Fonseca}, J.~R. {Gair}, M.~E. {Gonzalez},
%  E.~{Graikou}, L.~{Guillemot}, J.~W.~T. {Hessels}, G.~{Hobbs}, G.~H.
%  {Janssen}, G.~{Jones}, R.~{Karuppusamy}, M.~{Keith}, M.~{Kerr}, M.~{Kramer},
%  M.~T. {Lam}, P.~D. {Lasky}, A.~{Lassus}, P.~{Lazarus}, T.~J.~W. {Lazio},
%  K.~J. {Lee}, L.~{Levin}, K.~{Liu}, R.~S. {Lynch}, D.~R. {Madison},
%  J.~{McKee}, M.~{McLaughlin}, S.~T. {McWilliams}, C.~M.~F. {Mingarelli}, D.~J.
%  {Nice}, S.~{Os{\l}owski}, T.~T. {Pennucci}, B.~B.~P. {Perera}, D.~{Perrodin},
%  A.~{Petiteau}, A.~{Possenti}, S.~M. {Ransom}, D.~{Reardon}, P.~A. {Rosado},
%  S.~A. {Sanidas}, A.~{Sesana}, G.~{Shaifullah}, X.~{Siemens}, R.~{Smits},
%  I.~{Stairs}, B.~{Stappers}, D.~R. {Stinebring}, K.~{Stovall}, J.~{Swiggum},
%  \textbf{{Taylor}, S.~R.}, G.~{Theureau}, C.~{Tiburzi}, L.~{Toomey},
%  M.~{Vallisneri}, W.~{van Straten}, A.~{Vecchio}, J.-B. {Wang}, Y.~{Wang},
%  X.~P. {You}, W.~W. {Zhu}, and X.-J. {Zhu}.
%\newblock {\emph{``From spin noise to systematics: stochastic processes in the first
%  International Pulsar Timing Array data release"}}.
%\newblock {\emph \mnras}, 458:2161--2187, May 2016.
%
%\bibitem{vlh+16}
%J.~P.~W. {Verbiest}, L.~{Lentati}, G.~{Hobbs}, R.~{van Haasteren}, P.~B.
%  {Demorest}, G.~H. {Janssen}, J.-B. {Wang}, G.~{Desvignes}, R.~N. {Caballero},
%  M.~J. {Keith}, D.~J. {Champion}, Z.~{Arzoumanian}, S.~{Babak}, C.~G. {Bassa},
%  N.~D.~R. {Bhat}, A.~{Brazier}, P.~{Brem}, M.~{Burgay}, S.~{Burke-Spolaor},
%  S.~J. {Chamberlin}, S.~{Chatterjee}, B.~{Christy}, I.~{Cognard}, J.~M.
%  {Cordes}, S.~{Dai}, T.~{Dolch}, J.~A. {Ellis}, R.~D. {Ferdman}, E.~{Fonseca},
%  J.~R. {Gair}, N.~E. {Garver-Daniels}, P.~{Gentile}, M.~E. {Gonzalez},
%  E.~{Graikou}, L.~{Guillemot}, J.~W.~T. {Hessels}, G.~{Jones},
%  R.~{Karuppusamy}, M.~{Kerr}, M.~{Kramer}, M.~T. {Lam}, P.~D. {Lasky},
%  A.~{Lassus}, P.~{Lazarus}, T.~J.~W. {Lazio}, K.~J. {Lee}, L.~{Levin},
%  K.~{Liu}, R.~S. {Lynch}, A.~G. {Lyne}, J.~{Mckee}, M.~A. {McLaughlin}, S.~T.
%  {McWilliams}, D.~R. {Madison}, R.~N. {Manchester}, C.~M.~F. {Mingarelli},
%  D.~J. {Nice}, S.~{Os{\l}owski}, N.~T. {Palliyaguru}, T.~T. {Pennucci},
%  B.~B.~P. {Perera}, D.~{Perrodin}, A.~{Possenti}, A.~{Petiteau}, S.~M.
%  {Ransom}, D.~{Reardon}, P.~A. {Rosado}, S.~A. {Sanidas}, A.~{Sesana},
%  G.~{Shaifullah}, R.~M. {Shannon}, X.~{Siemens}, J.~{Simon}, R.~{Smits},
%  R.~{Spiewak}, I.~H. {Stairs}, B.~W. {Stappers}, D.~R. {Stinebring},
%  K.~{Stovall}, J.~K. {Swiggum}, \textbf{{Taylor}, S.~R.}, G.~{Theureau},
%  C.~{Tiburzi}, L.~{Toomey}, M.~{Vallisneri}, W.~{van Straten}, A.~{Vecchio},
%  Y.~{Wang}, L.~{Wen}, X.~P. {You}, W.~W. {Zhu}, and X.-J. {Zhu}.
%\newblock {\emph{``The International Pulsar Timing Array: First data release"}}.
%\newblock {\emph \mnras}, 458:1267--1288, May 2016.
%
%\bibitem{arz+16}
%Z.~{Arzoumanian}, A.~{Brazier}, S.~{Burke-Spolaor}, S.~J. {Chamberlin},
%  S.~{Chatterjee}, B.~{Christy}, J.~M. {Cordes}, N.~J. {Cornish}, K.~{Crowter},
%  P.~B. {Demorest}, X.~{Deng}, T.~{Dolch}, J.~A. {Ellis}, R.~D. {Ferdman},
%  E.~{Fonseca}, N.~{Garver-Daniels}, M.~E. {Gonzalez}, F.~{Jenet}, G.~{Jones},
%  M.~L. {Jones}, V.~M. {Kaspi}, M.~{Koop}, M.~T. {Lam}, T.~J.~W. {Lazio},
%  L.~{Levin}, A.~N. {Lommen}, D.~R. {Lorimer}, J.~{Luo}, R.~S. {Lynch}, D.~R.
%  {Madison}, M.~A. {McLaughlin}, S.~T. {McWilliams}, C.~M.~F. {Mingarelli},
%  D.~J. {Nice}, N.~{Palliyaguru}, T.~T. {Pennucci}, S.~M. {Ransom},
%  L.~{Sampson}, S.~A. {Sanidas}, A.~{Sesana}, X.~{Siemens}, J.~{Simon}, I.~H.
%  {Stairs}, D.~R. {Stinebring}, K.~{Stovall}, J.~{Swiggum}, \textbf{{Taylor},
%  S.~R.}, M.~{Vallisneri}, R.~{van Haasteren}, Y.~{Wang}, W.~W. {Zhu}, and {The
%  NANOGrav Collaboration}.
%\newblock {\emph{``The NANOGrav Nine-year Data Set: Limits on the Isotropic Stochastic
%  Gravitational Wave Background"}}.
%\newblock {\emph \apj}, 821:13, April 2016.
%
%\bibitem{cll+16}
%R.~N. {Caballero}, K.~J. {Lee}, L.~{Lentati}, G.~{Desvignes}, D.~J. {Champion},
%  J.~P.~W. {Verbiest}, G.~H. {Janssen}, B.~W. {Stappers}, M.~{Kramer},
%  P.~{Lazarus}, A.~{Possenti}, C.~{Tiburzi}, D.~{Perrodin}, S.~{Os{\l}owski},
%  S.~{Babak}, C.~G. {Bassa}, P.~{Brem}, M.~{Burgay}, I.~{Cognard}, J.~R.
%  {Gair}, E.~{Graikou}, L.~{Guillemot}, J.~W.~T. {Hessels}, R.~{Karuppusamy},
%  A.~{Lassus}, K.~{Liu}, J.~{McKee}, C.~M.~F. {Mingarelli}, A.~{Petiteau},
%  M.~B. {Purver}, P.~A. {Rosado}, S.~{Sanidas}, A.~{Sesana}, G.~{Shaifullah},
%  R.~{Smits}, \textbf{{Taylor}, S.~R.}, G.~{Theureau}, R.~{van Haasteren}, and
%  A.~{Vecchio}.
%\newblock {\emph{``The noise properties of 42 millisecond pulsars from the European
%  Pulsar Timing Array and their impact on gravitational-wave searches"}}.
%\newblock {\emph \mnras}, 457:4421--4440, April 2016.
%
%\bibitem{bps+16}
%S.~{Babak}, A.~{Petiteau}, A.~{Sesana}, P.~{Brem}, P.~A. {Rosado},
%  \textbf{{Taylor}, S.~R.}, A.~{Lassus}, J.~W.~T. {Hessels}, C.~G. {Bassa},
%  M.~{Burgay}, R.~N. {Caballero}, D.~J. {Champion}, I.~{Cognard},
%  G.~{Desvignes}, J.~R. {Gair}, L.~{Guillemot}, G.~H. {Janssen},
%  R.~{Karuppusamy}, M.~{Kramer}, P.~{Lazarus}, K.~J. {Lee}, L.~{Lentati},
%  K.~{Liu}, C.~M.~F. {Mingarelli}, S.~{Os{\l}owski}, D.~{Perrodin},
%  A.~{Possenti}, M.~B. {Purver}, S.~{Sanidas}, R.~{Smits}, B.~{Stappers},
%  G.~{Theureau}, C.~{Tiburzi}, R.~{van Haasteren}, A.~{Vecchio}, and J.~P.~W.
%  {Verbiest}.
%\newblock {\emph{``European Pulsar Timing Array limits on continuous gravitational
%  waves from individual supermassive black hole binaries"}}.
%\newblock {\emph \mnras}, 455:1665--1679, January 2016.
%
%\bibitem{grt15}
%J.~R. {Gair}, J.~D. {Romano}, and \textbf{{Taylor}, S.~R.}
%\newblock {\emph{``Mapping gravitational-wave backgrounds of arbitrary polarisation
%  using pulsar timing arrays"}}.
%\newblock {\emph \prd}, 92(10):102003, November 2015.
%
%\bibitem{ltm+15}
%L.~{Lentati}, \textbf{{Taylor}, S.~R.}, C.~M.~F. {Mingarelli}, A.~{Sesana},
%  S.~A. {Sanidas}, A.~{Vecchio}, R.~N. {Caballero}, K.~J. {Lee}, R.~{van
%  Haasteren}, S.~{Babak}, C.~G. {Bassa}, P.~{Brem}, M.~{Burgay}, D.~J.
%  {Champion}, I.~{Cognard}, G.~{Desvignes}, J.~R. {Gair}, L.~{Guillemot},
%  J.~W.~T. {Hessels}, G.~H. {Janssen}, R.~{Karuppusamy}, M.~{Kramer},
%  A.~{Lassus}, P.~{Lazarus}, K.~{Liu}, S.~{Os{\l}owski}, D.~{Perrodin},
%  A.~{Petiteau}, A.~{Possenti}, M.~B. {Purver}, P.~A. {Rosado}, R.~{Smits},
%  B.~{Stappers}, G.~{Theureau}, C.~{Tiburzi}, and J.~P.~W. {Verbiest}.
%\newblock {\emph{``European Pulsar Timing Array limits on an isotropic stochastic
%  gravitational-wave background"}}.
%\newblock {\emph \mnras}, 453:2576--2598, November 2015.
%
%\bibitem{hmgt15}
%E.~A. {Huerta}, S.~T. {McWilliams}, J.~R. {Gair}, and \textbf{{Taylor}, S.~R.}
%\newblock {\emph{``Detection of eccentric supermassive black hole binaries with pulsar
%  timing arrays: Signal-to-noise ratio calculations"}}.
%\newblock {\emph \prd}, 92(6):063010, September 2015.
%
%\bibitem{rtc+15}
%J.~D. {Romano}, \textbf{{Taylor}, S.~R.}, N.~J. {Cornish}, J.~{Gair}, C.~M.~F.
%  {Mingarelli}, and R.~{van Haasteren}.
%\newblock {\emph{``Phase-coherent mapping of gravitational-wave backgrounds using
%  ground-based laser interferometers"}}.
%\newblock {\emph \prd}, 92(4):042003, August 2015.
%
%\bibitem{mtg15}
%C.~J. {Moore}, \textbf{{Taylor}, S.~R.}, and J.~R. {Gair}.
%\newblock {\emph{``Estimating the sensitivity of pulsar timing arrays"}}.
%\newblock {\emph Classical and Quantum Gravity}, 32(5):055004, March 2015.
%
%\bibitem{grtm14}
%J.~{Gair}, J.~D. {Romano}, \textbf{{Taylor}, S.}, and C.~M.~F. {Mingarelli}.
%\newblock {\emph{``Mapping gravitational-wave backgrounds using methods from CMB
%  analysis: Application to pulsar timing arrays"}}.
%\newblock {\emph \prd}, 90(8):082001, October 2014.
%
%\bibitem{lah+13}
%L.~{Lentati}, P.~{Alexander}, M.~P. {Hobson}, \textbf{{Taylor}, S.}, J.~{Gair},
%  S.~T. {Balan}, and R.~{van Haasteren}.
%\newblock {\emph{``Hyper-efficient model-independent Bayesian method for the analysis
%  of pulsar timing data"}}.
%\newblock {\emph \prd}, 87(10):104021, May 2013.
%
%\end{thebibliography}

%----------------------------------------------------------------------------------------
%   COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{OS}{Linux/Unix, Windows}
\cvitem{Programming}{C/C++, \textsc{Python}, UNIX shell scripting, particle-swarm algorithms, Monte Carlo and nested sampling algorithms}
\cvitem{Typography}{\LaTeX, Bibtex, Microsoft Office, Pages, OpenOffice}
\cvitem{Scientific}{Mathematica, Matlab, \textsc{Python}}
\cvitem{GPU Programming}{CUDA C, PyCUDA}

%----------------------------------------------------------------------------------------
%   COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{References}

\cvitem{}{Available upon request.}


%----------------------------------------------------------------------------------------
%   COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}